### 2023-08-25 ASTR513/HW/HW1/src/main.tex
add some homeworks from the semester so far

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[margin=1in, headsep=36pt]{geometry}
\usepackage{hyperref}

\def\title{Homework 1}
\def\author{Noah Franz}
\def\duedate{August 28, 2023}
\def\class{ASTR513}

\fancypagestyle{hdr}
{
    \fancyhead[L]{\fontsize{16}{18}\selectfont \author \\ Due Date: \duedate }
    \fancyhead[R]{\fontsize{16}{18}\selectfont  \title \\ \class}
}

\begin{document}

\thispagestyle{hdr}

\section*{My Definitions of Statistics}
\begin{enumerate}
\item \textit{General:} Mathematical tools for summarizing data and quantifying uncertainty to help better understand and describe the real world.
\item \textit{Specific to Astrophysics:} Mathematical tools that provide methods to describe uncertainty in observational data and connect it with theoretical astrophysical models.
\end{enumerate}

\section*{ChatGPT Definitions of Statistics}
\begin{enumerate}
\item \textit{General:}
\begin{itemize}
\item \textit{Prompt:} Give a general definition of statistics in 1-2 sentences
\item \textit{Answer:} Statistics is the study of collecting, analyzing, interpreting, and presenting data to understand patterns, relationships, and trends within a given context.
\end{itemize}
\item \textit{Specific to Astrophysics:}
\begin{itemize}
\item \textit{Prompt:} Give a definition of statistics in the context of astrophysics in 1-2 sentences
\item \textit{Answer:} In the context of astrophysics, statistics involves the application of mathematical techniques to analyze and interpret astronomical data, helping researchers uncover patterns, distributions, and relationships among celestial objects and phenomena within the universe.
\end{itemize}
\end{enumerate}

\section*{Frequentist vs. Bayesian Statistics}
The three primary differences between the frequentist and bayesian interpretations of statistics are \cite{bayes_vs_frequentist}:

\begin{enumerate}
    \item In bayesian statistics, the parameters are random variables that can be tuned to see the likelihood of the underlying hypothesis given prior knowledge and the data. In frequentist statistics the theoretical parameters are fixed and the data is a random subset of the true distribution.
    \item Frequentist statistics uses confidence intervals to give a range that contains that percentage of observations when the experiment is repeated a large number of times. Bayesian statistics gives a a probability that the true value lies within the associated range of values.
    \item Frequentist statistics uses p-value to describe the probability that the observation is extreme compared a set of similar observations. Bayesian statistics uses the probability that the theoretical model, or hypothesis, agrees with the data. In other words, Bayesian statistics allows the comparison of data and theoretical models while frequentist statistics only allows the rejection of a null-hypothesis.
\end{enumerate}

\bibliographystyle{plain}
\bibliography{main}

\end{document}

### 2024-11-19 ASTR540/hw4/Franz_ASTR540_HW4_NB.tex
nb -> pdf for submission

\documentclass[11pt]{article}

    \usepackage[breakable]{tcolorbox}
    \usepackage{parskip} % Stop auto-indenting (to mimic markdown behaviour)

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % Maintain compatibility with old templates. Remove in nbconvert 6.0
    \let\Oldincludegraphics\includegraphics
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionFormat{nocaption}{}
    \captionsetup{format=nocaption,aboveskip=0pt,belowskip=0pt}

    \usepackage{float}
    \floatplacement{figure}{H} % forces figures to be placed at the correct location
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro

    \usepackage{iftex}
    \ifPDFTeX
        \usepackage[T1]{fontenc}
        \IfFileExists{alphabeta.sty}{
              \usepackage{alphabeta}
          }{
              \usepackage[mathletters]{ucs}
              \usepackage[utf8x]{inputenc}
          }
    \else
        \usepackage{fontspec}
        \usepackage{unicode-math}
    \fi

    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics
                         % to support a larger range
    \makeatletter % fix for old versions of grffile with XeLaTeX
    \@ifpackagelater{grffile}{2019/11/01}
    {
      % Do nothing on new versions
    }
    {
      \def\Gread@@xetex#1{%
        \IfFileExists{"\Gin@base".bb}%
        {\Gread@eps{\Gin@base.bb}}%
        {\Gread@@xetex@aux#1}%
      }
    }
    \makeatother
    \usepackage[Export]{adjustbox} % Used to constrain images to a maximum size
    \adjustboxset{max size={0.9\linewidth}{0.9\paperheight}}

    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    % The default LaTeX title has an obnoxious amount of whitespace. By default,
    % titling removes some of it. It also provides customization options.
    \usepackage{titling}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage{array}     % table support for pandoc >= 2.11.3
    \usepackage{calc}      % table minipage width calculation for pandoc >= 2.11.1
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines
    \usepackage{mathrsfs}

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}
    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
    \definecolor{ansi-default-inverse-bg}{HTML}{000000}

    % common color for the border for error outputs.
    \definecolor{outerrorbackground}{HTML}{FFDFDF}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatibility definitions
    \def\gt{>}
    \def\lt{<}
    \let\Oldtex\TeX
    \let\Oldlatex\LaTeX
    \renewcommand{\TeX}{\textrm{\Oldtex}}
    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
    % Document parameters
    % Document title
    \title{Franz\_ASTR540\_HW4\_NB}

% Pygments definitions
\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\@namedef{PY@tok@w}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\@namedef{PY@tok@c}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@cp}{\def\PY@tc##1{\textcolor[rgb]{0.61,0.40,0.00}{##1}}}
\@namedef{PY@tok@k}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kp}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kt}{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\@namedef{PY@tok@o}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@ow}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\@namedef{PY@tok@nb}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@nf}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\@namedef{PY@tok@nc}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\@namedef{PY@tok@nn}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\@namedef{PY@tok@ne}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.80,0.25,0.22}{##1}}}
\@namedef{PY@tok@nv}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@no}{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\@namedef{PY@tok@nl}{\def\PY@tc##1{\textcolor[rgb]{0.46,0.46,0.00}{##1}}}
\@namedef{PY@tok@ni}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.44,0.44,0.44}{##1}}}
\@namedef{PY@tok@na}{\def\PY@tc##1{\textcolor[rgb]{0.41,0.47,0.13}{##1}}}
\@namedef{PY@tok@nt}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@nd}{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\@namedef{PY@tok@s}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@sd}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@si}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.64,0.35,0.47}{##1}}}
\@namedef{PY@tok@se}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.36,0.12}{##1}}}
\@namedef{PY@tok@sr}{\def\PY@tc##1{\textcolor[rgb]{0.64,0.35,0.47}{##1}}}
\@namedef{PY@tok@ss}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@sx}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@m}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@gh}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\@namedef{PY@tok@gu}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\@namedef{PY@tok@gd}{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\@namedef{PY@tok@gi}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.52,0.00}{##1}}}
\@namedef{PY@tok@gr}{\def\PY@tc##1{\textcolor[rgb]{0.89,0.00,0.00}{##1}}}
\@namedef{PY@tok@ge}{\let\PY@it=\textit}
\@namedef{PY@tok@gs}{\let\PY@bf=\textbf}
\@namedef{PY@tok@gp}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\@namedef{PY@tok@go}{\def\PY@tc##1{\textcolor[rgb]{0.44,0.44,0.44}{##1}}}
\@namedef{PY@tok@gt}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\@namedef{PY@tok@err}{\def\PY@bc##1{{\setlength{\fboxsep}{\string -\fboxrule}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}}
\@namedef{PY@tok@kc}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kd}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kn}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kr}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@bp}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@fm}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\@namedef{PY@tok@vc}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@vg}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@vi}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@vm}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@sa}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@sb}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@sc}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@dl}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@s2}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@sh}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@s1}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@mb}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@mf}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@mh}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@mi}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@il}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@mo}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@ch}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@cm}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@cpf}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@c1}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@cs}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % For linebreaks inside Verbatim environment from package fancyvrb.
    \makeatletter
        \newbox\Wrappedcontinuationbox
        \newbox\Wrappedvisiblespacebox
        \newcommand*\Wrappedvisiblespace {\textcolor{red}{\textvisiblespace}}
        \newcommand*\Wrappedcontinuationsymbol {\textcolor{red}{\llap{\tiny$\m@th\hookrightarrow$}}}
        \newcommand*\Wrappedcontinuationindent {3ex }
        \newcommand*\Wrappedafterbreak {\kern\Wrappedcontinuationindent\copy\Wrappedcontinuationbox}
        % Take advantage of the already applied Pygments mark-up to insert
        % potential linebreaks for TeX processing.
        %        {, <, #, %, $, ' and ": go to next line.
        %        _, }, ^, &, >, - and ~: stay at end of broken line.
        % Use of \textquotesingle for straight quote.
        \newcommand*\Wrappedbreaksatspecials {%
            \def\PYGZus{\discretionary{\char`\_}{\Wrappedafterbreak}{\char`\_}}%
            \def\PYGZob{\discretionary{}{\Wrappedafterbreak\char`\{}{\char`\{}}%
            \def\PYGZcb{\discretionary{\char`\}}{\Wrappedafterbreak}{\char`\}}}%
            \def\PYGZca{\discretionary{\char`\^}{\Wrappedafterbreak}{\char`\^}}%
            \def\PYGZam{\discretionary{\char`\&}{\Wrappedafterbreak}{\char`\&}}%
            \def\PYGZlt{\discretionary{}{\Wrappedafterbreak\char`\<}{\char`\<}}%
            \def\PYGZgt{\discretionary{\char`\>}{\Wrappedafterbreak}{\char`\>}}%
            \def\PYGZsh{\discretionary{}{\Wrappedafterbreak\char`\#}{\char`\#}}%
            \def\PYGZpc{\discretionary{}{\Wrappedafterbreak\char`\%}{\char`\%}}%
            \def\PYGZdl{\discretionary{}{\Wrappedafterbreak\char`\$}{\char`\$}}%
            \def\PYGZhy{\discretionary{\char`\-}{\Wrappedafterbreak}{\char`\-}}%
            \def\PYGZsq{\discretionary{}{\Wrappedafterbreak\textquotesingle}{\textquotesingle}}%
            \def\PYGZdq{\discretionary{}{\Wrappedafterbreak\char`\"}{\char`\"}}%
            \def\PYGZti{\discretionary{\char`\~}{\Wrappedafterbreak}{\char`\~}}%
        }
        % Some characters . , ; ? ! / are not pygmentized.
        % This macro makes them "active" and they will insert potential linebreaks
        \newcommand*\Wrappedbreaksatpunct {%
            \lccode`\~`\.\lowercase{\def~}{\discretionary{\hbox{\char`\.}}{\Wrappedafterbreak}{\hbox{\char`\.}}}%
            \lccode`\~`\,\lowercase{\def~}{\discretionary{\hbox{\char`\,}}{\Wrappedafterbreak}{\hbox{\char`\,}}}%
            \lccode`\~`\;\lowercase{\def~}{\discretionary{\hbox{\char`\;}}{\Wrappedafterbreak}{\hbox{\char`\;}}}%
            \lccode`\~`\:\lowercase{\def~}{\discretionary{\hbox{\char`\:}}{\Wrappedafterbreak}{\hbox{\char`\:}}}%
            \lccode`\~`\?\lowercase{\def~}{\discretionary{\hbox{\char`\?}}{\Wrappedafterbreak}{\hbox{\char`\?}}}%
            \lccode`\~`\!\lowercase{\def~}{\discretionary{\hbox{\char`\!}}{\Wrappedafterbreak}{\hbox{\char`\!}}}%
            \lccode`\~`\/\lowercase{\def~}{\discretionary{\hbox{\char`\/}}{\Wrappedafterbreak}{\hbox{\char`\/}}}%
            \catcode`\.\active
            \catcode`\,\active
            \catcode`\;\active
            \catcode`\:\active
            \catcode`\?\active
            \catcode`\!\active
            \catcode`\/\active
            \lccode`\~`\~
        }
    \makeatother

    \let\OriginalVerbatim=\Verbatim
    \makeatletter
    \renewcommand{\Verbatim}[1][1]{%
        %\parskip\z@skip
        \sbox\Wrappedcontinuationbox {\Wrappedcontinuationsymbol}%
        \sbox\Wrappedvisiblespacebox {\FV@SetupFont\Wrappedvisiblespace}%
        \def\FancyVerbFormatLine ##1{\hsize\linewidth
            \vtop{\raggedright\hyphenpenalty\z@\exhyphenpenalty\z@
                \doublehyphendemerits\z@\finalhyphendemerits\z@
                \strut ##1\strut}%
        }%
        % If the linebreak is at a space, the latter will be displayed as visible
        % space at end of first line, and a continuation symbol starts next line.
        % Stretch/shrink are however usually zero for typewriter font.
        \def\FV@Space {%
            \nobreak\hskip\z@ plus\fontdimen3\font minus\fontdimen4\font
            \discretionary{\copy\Wrappedvisiblespacebox}{\Wrappedafterbreak}
            {\kern\fontdimen2\font}%
        }%

        % Allow breaks at special characters using \PYG... macros.
        \Wrappedbreaksatspecials
        % Breaks at punctuation characters . , ; ? ! and / need catcode=\active
        \OriginalVerbatim[#1,codes*=\Wrappedbreaksatpunct]%
    }
    \makeatother

    % Exact colors from NB
    \definecolor{incolor}{HTML}{303F9F}
    \definecolor{outcolor}{HTML}{D84315}
    \definecolor{cellborder}{HTML}{CFCFCF}
    \definecolor{cellbackground}{HTML}{F7F7F7}

    % prompt
    \makeatletter
    \newcommand{\boxspacing}{\kern\kvtcb@left@rule\kern\kvtcb@boxsep}
    \makeatother
    \newcommand{\prompt}[4]{
        {\ttfamily\llap{{\color{#2}[#3]:\hspace{3pt}#4}}\vspace{-\baselineskip}}
    }

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

\begin{document}

    \maketitle

    \section{ASTR540 Homework 4}\label{astr540-homework-4}

Noah Franz

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{1}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{import} \PY{n+nn}{warnings}
\PY{k+kn}{from} \PY{n+nn}{functools} \PY{k+kn}{import} \PY{n}{partial}
\PY{k+kn}{from} \PY{n+nn}{copy} \PY{k+kn}{import} \PY{n}{deepcopy}

\PY{k+kn}{import} \PY{n+nn}{pandas} \PY{k}{as} \PY{n+nn}{pd}
\PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k}{as} \PY{n+nn}{np}
\PY{k+kn}{import} \PY{n+nn}{matplotlib}\PY{n+nn}{.}\PY{n+nn}{pyplot} \PY{k}{as} \PY{n+nn}{plt}

\PY{k+kn}{from} \PY{n+nn}{astropy}\PY{n+nn}{.}\PY{n+nn}{coordinates} \PY{k+kn}{import} \PY{n}{SkyCoord}
\PY{k+kn}{from} \PY{n+nn}{astropy} \PY{k+kn}{import} \PY{n}{units} \PY{k}{as} \PY{n}{u}
\PY{k+kn}{from} \PY{n+nn}{astropy} \PY{k+kn}{import} \PY{n}{constants} \PY{k}{as} \PY{n}{c}
\PY{k+kn}{from} \PY{n+nn}{astropy}\PY{n+nn}{.}\PY{n+nn}{table} \PY{k+kn}{import} \PY{n}{vstack}

\PY{k+kn}{from} \PY{n+nn}{astroquery}\PY{n+nn}{.}\PY{n+nn}{gaia} \PY{k+kn}{import} \PY{n}{Gaia}
\PY{k+kn}{from} \PY{n+nn}{astroquery}\PY{n+nn}{.}\PY{n+nn}{sdss} \PY{k+kn}{import} \PY{n}{SDSS}
\end{Verbatim}
\end{tcolorbox}

    \subsection{Problem 1}\label{problem-1}

Proper Motion of Bo ̈otes III. Let's revisit the proper motion of the
disrupting satellite Bo ̈otes III, as discussed in Carlin \& Sand 2018.
Since that study, there has been the 3rd data release of Gaia (Gaia
DR3), so it is possible that there are more proper motion members in the
catalog, and that the overall uncertainties have improved.

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\item
  First, go to Table 1 of the Carlin paper, which displays all of the
  `radial velocity confirmed' members of Bo ̈otes III, and make your own
  table with updated proper motion values.
\item
  By how much have the uncertainties going from Gaia DR2 to Gaia DR3
  improved? Have there been any large changes in proper motion for any
  of these stars (\textgreater5σ)? \textbar{}
\item
  Calculate your own error-weighted proper motion to Bo ̈otes III,
  compare it with the DR2 value, and make a plot similar to Figure 1 of
  the paper.
\item
  Try to identify further proper motion members in Bo ̈otes III, as
  described in Section 2.3 of the paper. Do the improved measurements of
  Gaia DR3 lead to more plausible proper motion members of Bo ̈otes III?
\end{enumerate}

\subsubsection{Problem 1a}\label{problem-1a}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{2}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} read in the Table 1 data from Carin \PYZam{} Sand (2018)}
\PY{n}{data\PYZus{}dr2} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{read\PYZus{}csv}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Carlin\PYZus{}and\PYZus{}Sand\PYZus{}2018\PYZus{}Table1.txt}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{sep}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{c+c1}{\PYZsh{} and then clean it up}
\PY{n}{data\PYZus{}dr2} \PY{o}{=} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{n}{how}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{all}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}

\PY{n}{data\PYZus{}dr2} \PY{o}{=} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{replace}\PY{p}{(}\PY{p}{\PYZob{}}
    \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{cdots}\PY{l+s+s2}{\PYZdq{}}\PY{p}{:} \PY{n}{np}\PY{o}{.}\PY{n}{nan}\PY{p}{,}
    \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{N}\PY{l+s+s2}{\PYZdq{}} \PY{p}{:} \PY{k+kc}{False}\PY{p}{,}
    \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Y}\PY{l+s+s2}{\PYZdq{}} \PY{p}{:} \PY{k+kc}{True}
\PY{p}{\PYZcb{}}\PY{p}{)}

\PY{n}{data\PYZus{}dr2}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{v\PYZus{}helio\PYZus{}err}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{v}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ +or\PYZhy{} }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]} \PY{k}{if} \PY{o+ow}{not} \PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{v}\PY{p}{)} \PY{k}{else} \PY{n}{v} \PY{k}{for} \PY{n}{v} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{v\PYZus{}helio}\PY{p}{]}
\PY{n}{data\PYZus{}dr2}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{v\PYZus{}helio}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{v}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ +or\PYZhy{} }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]} \PY{k}{if} \PY{o+ow}{not} \PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{v}\PY{p}{)} \PY{k}{else} \PY{n}{v} \PY{k}{for} \PY{n}{v} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{v\PYZus{}helio}\PY{p}{]}

\PY{n}{data\PYZus{}dr2}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mu\PYZus{}alpha\PYZus{}err}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{v}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ +or\PYZhy{} }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}  \PY{k}{if} \PY{o+ow}{not} \PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{v}\PY{p}{)} \PY{k}{else} \PY{n}{v} \PY{k}{for} \PY{n}{v} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{mu\PYZus{}alpha}\PY{p}{]}
\PY{n}{data\PYZus{}dr2}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mu\PYZus{}alpha}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{v}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ +or\PYZhy{} }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}  \PY{k}{if} \PY{o+ow}{not} \PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{v}\PY{p}{)} \PY{k}{else} \PY{n}{v} \PY{k}{for} \PY{n}{v} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{mu\PYZus{}alpha}\PY{p}{]}

\PY{n}{data\PYZus{}dr2}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mu\PYZus{}delta\PYZus{}err}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{v}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ +or\PYZhy{} }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}  \PY{k}{if} \PY{o+ow}{not} \PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{v}\PY{p}{)} \PY{k}{else} \PY{n}{v} \PY{k}{for} \PY{n}{v} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{mu\PYZus{}delta}\PY{p}{]}
\PY{n}{data\PYZus{}dr2}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mu\PYZus{}delta}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{p}{[}\PY{n}{v}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ +or\PYZhy{} }\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}  \PY{k}{if} \PY{o+ow}{not} \PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{v}\PY{p}{)} \PY{k}{else} \PY{n}{v} \PY{k}{for} \PY{n}{v} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{mu\PYZus{}delta}\PY{p}{]}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{3}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{data\PYZus{}dr3} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\PY{n}{idxs} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\PY{n}{radius} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{*}\PY{n}{u}\PY{o}{.}\PY{n}{arcsec}

\PY{k}{for} \PY{n}{i}\PY{p}{,} \PY{n}{row} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{iterrows}\PY{p}{(}\PY{p}{)}\PY{p}{:}
    \PY{n}{coord} \PY{o}{=} \PY{n}{SkyCoord}\PY{p}{(}\PY{n}{row}\PY{o}{.}\PY{n}{alpha}\PY{p}{,} \PY{n}{row}\PY{o}{.}\PY{n}{delta}\PY{p}{,} \PY{n}{unit}\PY{o}{=}\PY{n}{u}\PY{o}{.}\PY{n}{deg}\PY{p}{)}
    \PY{n}{job} \PY{o}{=} \PY{n}{Gaia}\PY{o}{.}\PY{n}{cone\PYZus{}search}\PY{p}{(}\PY{n}{coord}\PY{p}{,} \PY{n}{radius}\PY{o}{=}\PY{n}{radius}\PY{p}{)}
    \PY{n}{res} \PY{o}{=} \PY{n}{job}\PY{o}{.}\PY{n}{get\PYZus{}results}\PY{p}{(}\PY{p}{)}

    \PY{k}{if} \PY{n+nb}{len}\PY{p}{(}\PY{n}{res}\PY{p}{)} \PY{o}{!=} \PY{l+m+mi}{1}\PY{p}{:}
        \PY{n}{warnings}\PY{o}{.}\PY{n}{warn}\PY{p}{(}\PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Length of result not equal to 1 for }\PY{l+s+si}{\PYZob{}}\PY{n}{row}\PY{o}{.}\PY{n}{source\PYZus{}id}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{!}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
        \PY{k}{continue}

    \PY{n}{data\PYZus{}dr3}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{res}\PY{p}{)}
    \PY{n}{idxs}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{i}\PY{p}{)} \PY{c+c1}{\PYZsh{} keep track of index for joining}

\PY{n}{data\PYZus{}dr3} \PY{o}{=} \PY{n}{vstack}\PY{p}{(}\PY{n}{data\PYZus{}dr3}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}pandas}\PY{p}{(}\PY{p}{)}
\PY{n}{data\PYZus{}dr3} \PY{o}{=} \PY{n}{data\PYZus{}dr3}\PY{o}{.}\PY{n}{set\PYZus{}index}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{idxs}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
/tmp/ipykernel\_466903/39562995.py:11: UserWarning: Length of result not equal to
1 for -9223372036854775808!
  warnings.warn(f"Length of result not equal to 1 for \{row.source\_id\}!")
    \end{Verbatim}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{4}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{data\PYZus{}dr3}\PY{o}{.}\PY{n}{columns} \PY{o}{=} \PY{p}{[}\PY{n}{c}\PY{o}{+}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}}  \PY{k}{if} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}} \PY{o+ow}{not} \PY{o+ow}{in} \PY{n}{c} \PY{k}{else} \PY{n}{c} \PY{k}{for} \PY{n}{c} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr3}\PY{o}{.}\PY{n}{columns}\PY{p}{]}
\PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{columns} \PY{o}{=} \PY{p}{[}\PY{n}{c}\PY{o}{+}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZus{}dr2}\PY{l+s+s2}{\PYZdq{}} \PY{k}{if} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZus{}dr2}\PY{l+s+s2}{\PYZdq{}} \PY{o+ow}{not} \PY{o+ow}{in} \PY{n}{c} \PY{k}{else} \PY{n}{c} \PY{k}{for} \PY{n}{c} \PY{o+ow}{in} \PY{n}{data\PYZus{}dr2}\PY{o}{.}\PY{n}{columns}\PY{p}{]}

\PY{n}{data} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{merge}\PY{p}{(}\PY{n}{data\PYZus{}dr2}\PY{p}{,} \PY{n}{data\PYZus{}dr3}\PY{p}{,} \PY{n}{left\PYZus{}index}\PY{o}{=}\PY{k+kc}{True}\PY{p}{,} \PY{n}{right\PYZus{}index}\PY{o}{=}\PY{k+kc}{True}\PY{p}{,} \PY{n}{how}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{outer}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{22}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{get\PYZus{}sdss\PYZus{}colors}\PY{p}{(}\PY{n}{df}\PY{p}{,} \PY{n}{ra\PYZus{}key}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ra}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{dec\PYZus{}key}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dec}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{filters}\PY{o}{=}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{u}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{g}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{r}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{i}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{z}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{p}{)}\PY{p}{:}

    \PY{n}{all\PYZus{}data} \PY{o}{=} \PY{p}{[}\PY{p}{]}

    \PY{k}{for} \PY{n}{idx}\PY{p}{,} \PY{n}{row} \PY{o+ow}{in} \PY{n}{df}\PY{o}{.}\PY{n}{iterrows}\PY{p}{(}\PY{p}{)}\PY{p}{:}

        \PY{n}{coord} \PY{o}{=} \PY{n}{SkyCoord}\PY{p}{(}\PY{n}{row}\PY{p}{[}\PY{n}{ra\PYZus{}key}\PY{p}{]}\PY{p}{,} \PY{n}{row}\PY{p}{[}\PY{n}{dec\PYZus{}key}\PY{p}{]}\PY{p}{,} \PY{n}{unit}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{deg}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

        \PY{k}{try}\PY{p}{:}
            \PY{n}{res} \PY{o}{=} \PY{n}{SDSS}\PY{o}{.}\PY{n}{query\PYZus{}region}\PY{p}{(}
                \PY{n}{coord}\PY{p}{,} 
                \PY{n}{radius}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{*}\PY{n}{u}\PY{o}{.}\PY{n}{arcsec}\PY{p}{,} 
                \PY{n}{spectro}\PY{o}{=}\PY{k+kc}{False}\PY{p}{,}
                \PY{n}{fields}\PY{o}{=}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ra}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dec}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{objid}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{+} \PY{n}{filters}\PY{p}{,}
            \PY{p}{)}
        \PY{k}{except} \PY{n+ne}{Exception} \PY{k}{as} \PY{n}{e}\PY{p}{:}
            \PY{n}{all\PYZus{}data}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{row}\PY{p}{)}
            \PY{k}{continue}

        \PY{k}{if} \PY{n}{res} \PY{o+ow}{is} \PY{k+kc}{None} \PY{o+ow}{or} \PY{o+ow}{not} \PY{n+nb}{len}\PY{p}{(}\PY{n}{res}\PY{p}{)}\PY{p}{:}
            \PY{n}{all\PYZus{}data}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{row}\PY{p}{)}
            \PY{n}{warnings}\PY{o}{.}\PY{n}{warn}\PY{p}{(}\PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Skipping }\PY{l+s+si}{\PYZob{}}\PY{n}{row}\PY{o}{.}\PY{n}{DESIGNATION}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{ because no SDSS data!}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
            \PY{k}{continue}

        \PY{n}{res} \PY{o}{=} \PY{n}{res}\PY{o}{.}\PY{n}{to\PYZus{}pandas}\PY{p}{(}\PY{p}{)}

        \PY{n}{res\PYZus{}filtered} \PY{o}{=} \PY{n}{res}\PY{p}{[}\PY{n}{res}\PY{o}{.}\PY{n}{g} \PY{o}{\PYZgt{}} \PY{o}{\PYZhy{}}\PY{l+m+mi}{100}\PY{p}{]}

        \PY{k}{if} \PY{o+ow}{not} \PY{n+nb}{len}\PY{p}{(}\PY{n}{res}\PY{p}{)}\PY{p}{:}
            \PY{n}{all\PYZus{}data}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{row}\PY{p}{)}
            \PY{n}{warnings}\PY{o}{.}\PY{n}{warn}\PY{p}{(}\PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Skipping }\PY{l+s+si}{\PYZob{}}\PY{n}{row}\PY{o}{.}\PY{n}{DESIGNATION}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{ because no high quality SDSS data!}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
            \PY{k}{continue}

        \PY{c+c1}{\PYZsh{} take the u, g, r, i, z from the closest row }
        \PY{n}{min\PYZus{}sep} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{argmin}\PY{p}{(}
            \PY{n}{coord}\PY{o}{.}\PY{n}{separation}\PY{p}{(}
                \PY{n}{SkyCoord}\PY{p}{(}
                    \PY{n}{res\PYZus{}filtered}\PY{o}{.}\PY{n}{ra}\PY{o}{.}\PY{n}{values}\PY{p}{,} 
                    \PY{n}{res\PYZus{}filtered}\PY{o}{.}\PY{n}{dec}\PY{o}{.}\PY{n}{values}\PY{p}{,} 
                    \PY{n}{unit}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{deg}\PY{l+s+s2}{\PYZdq{}}
                \PY{p}{)}
            \PY{p}{)}
        \PY{p}{)}
        \PY{k}{for} \PY{n}{filt} \PY{o+ow}{in} \PY{n}{filters}\PY{p}{:}
            \PY{n}{row}\PY{p}{[}\PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZob{}}\PY{n}{filt}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{\PYZus{}sdss}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{n}{res\PYZus{}filtered}\PY{p}{[}\PY{n}{filt}\PY{p}{]}\PY{o}{.}\PY{n}{values}\PY{p}{[}\PY{n}{min\PYZus{}sep}\PY{p}{]}

        \PY{n}{all\PYZus{}data}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{row}\PY{p}{)}

    \PY{k}{return} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{all\PYZus{}data}\PY{p}{)}

\PY{n}{data} \PY{o}{=} \PY{n}{get\PYZus{}sdss\PYZus{}colors}\PY{p}{(}\PY{n}{data}\PY{p}{,} \PY{n}{ra\PYZus{}key}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ra\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{dec\PYZus{}key}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dec\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{data}\PY{p}{[}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{source\PYZus{}id\PYZus{}dr2}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{alpha\PYZus{}dr2}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{delta\PYZus{}dr2}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mu\PYZus{}alpha\PYZus{}dr2}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{mu\PYZus{}delta\PYZus{}dr2}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{SOURCE\PYZus{}ID\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ra\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{dec\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{pmra\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{pmdec\PYZus{}dr3}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{p}{]}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{22}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
          source\_id\_dr2   alpha\_dr2  delta\_dr2 mu\_alpha\_dr2 mu\_delta\_dr2  \textbackslash{}
0   1450811159128205568  208.955653  26.502208        1.078        5.259
1   1450817000283805824  209.013621  26.661679       -0.466       -0.583
2   1450826552290908800  209.128453  26.840015       -1.211       -1.139
3   1450826724089602816  209.159600  26.872888        -1.84       -1.784
4   1451038792395234560  209.174766  26.979976       -1.932        0.579
5   1450823051893369984  209.261163  26.829991       -1.709       -0.332
6   1450803222028673280  209.331958  26.573608       -1.492       -0.928
7   1450833767836315392  209.467272  26.804392       -0.207       -0.927
8   1450828682594980736  209.479318  26.664838       -0.462       -0.479
9   1450835314024556544  209.500251  26.835870       -1.006       -1.389
10  1450748486965605760  209.520145  26.287895       -0.566       -1.793
11  1450842185972291840  209.573497  26.944967       -1.435        0.541
12  1450781163077088000  209.610213  26.651188        0.058       -1.044
13  1450782949783229824  209.668856  26.711657       -2.084       -2.503
14  1450751617997283840  209.681364  26.467320       -5.797       -2.153
15  1450739381635432192  209.700291  26.407019         0.24       -1.969
16  1450785045727265792  209.810712  26.693513       -1.595       -1.315
17  1450788584780752256  209.845448  26.753301       -7.457       -2.497
18  1450783774417361280  209.916855  26.655120      -10.529      -11.886
19 -9223372036854775808  209.489916  26.858467          NaN          NaN
20  1258556500130302080  210.143865  25.931296        -1.34       -0.978

    SOURCE\_ID\_dr3      ra\_dr3    dec\_dr3   pmra\_dr3  pmdec\_dr3
0    1.450811e+18  208.955653  26.502208  -1.957361  -2.901003
1    1.450817e+18  209.013621  26.661679  -1.147453  -0.904130
2    1.450827e+18  209.128453  26.840015  -0.837238  -0.971798
3    1.450827e+18  209.159600  26.872888  -0.857254  -1.206666
4    1.451039e+18  209.174766  26.979976  -1.652480  -0.706780
5    1.450823e+18  209.261163  26.829991  -1.400544  -1.098103
6    1.450803e+18  209.331957  26.573608  -1.378667  -0.721432
7    1.450834e+18  209.467272  26.804392  -1.324451  -0.947451
8    1.450829e+18  209.479318  26.664838  -0.470838  -0.927059
9    1.450835e+18  209.500250  26.835871  -1.611917  -0.534405
10   1.450748e+18  209.520145  26.287895  -0.832462  -1.081806
11   1.450842e+18  209.573497  26.944967  -1.064027  -0.821582
12   1.450781e+18  209.610213  26.651188  -0.600902  -0.834171
13   1.450783e+18  209.668855  26.711657  -3.194013  -1.795397
14   1.450752e+18  209.681363  26.467319  -4.928035  -3.255653
15   1.450739e+18  209.700291  26.407018  -0.215862  -3.008471
16   1.450785e+18  209.810711  26.693513  -1.239291  -1.117548
17   1.450789e+18  209.845446  26.753300  -7.274916  -2.051706
18   1.450784e+18  209.916853  26.655119 -11.452348  -7.981481
19            NaN         NaN        NaN        NaN        NaN
20   1.258557e+18  210.143865  25.931296  -1.235442  -0.889244
\end{Verbatim}
\end{tcolorbox}

    \subsubsection{Problem 1a Discussion}\label{problem-1a-discussion}

A summary of the results of merging the DR2 catalog from Carlin \& Sand
(2018) and the Gaia DR3 measurements of the same objects is shown in the
above table!

\subsubsection{Problem 1b}\label{problem-1b}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{6}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{fig}\PY{p}{,} \PY{n}{axs} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplots}\PY{p}{(}\PY{l+m+mi}{3}\PY{p}{,}\PY{l+m+mi}{2}\PY{p}{,}\PY{n}{figsize}\PY{o}{=}\PY{p}{(}\PY{l+m+mi}{16}\PY{p}{,}\PY{l+m+mi}{18}\PY{p}{)}\PY{p}{)}
\PY{n}{ax1}\PY{p}{,} \PY{n}{ax2}\PY{p}{,} \PY{n}{ax3}\PY{p}{,} \PY{n}{ax4}\PY{p}{,} \PY{n}{ax5}\PY{p}{,} \PY{n}{ax6} \PY{o}{=} \PY{n}{axs}\PY{o}{.}\PY{n}{flatten}\PY{p}{(}\PY{p}{)}

\PY{c+c1}{\PYZsh{} first plot the proper motion from DR2 to DR3}
\PY{n}{ax1}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}
    \PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}dr3}\PY{p}{,} 
    \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}alpha\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{xerr} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}error\PYZus{}dr3}\PY{p}{,}
    \PY{n}{yerr} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}alpha\PYZus{}err\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{none}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{color}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{k}\PY{l+s+s2}{\PYZdq{}}
\PY{p}{)}

\PY{n}{ax1}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{alpha\PYZdl{} (GAIA DR2)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax1}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{alpha\PYZdl{} (GAIA DR3)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{ylim} \PY{o}{=} \PY{n}{ax1}\PY{o}{.}\PY{n}{get\PYZus{}ylim}\PY{p}{(}\PY{p}{)}
\PY{n}{xlim} \PY{o}{=} \PY{n}{ax1}\PY{o}{.}\PY{n}{get\PYZus{}xlim}\PY{p}{(}\PY{p}{)}
\PY{n}{x}\PY{o}{=}\PY{n}{y}\PY{o}{=}\PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{o}{*}\PY{n}{ylim}\PY{p}{)}
\PY{n}{ax1}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,}\PY{n}{y}\PY{p}{,}\PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}\PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax1}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{n}{ylim}\PY{p}{)}
\PY{n}{ax1}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{n}{xlim}\PY{p}{)}

\PY{n}{ax2}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}
    \PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}dr3}\PY{p}{,} 
    \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}delta\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{xerr} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}error\PYZus{}dr3}\PY{p}{,}
    \PY{n}{yerr} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}delta\PYZus{}err\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{none}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{marker}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{o}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{color}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{k}\PY{l+s+s2}{\PYZdq{}}
\PY{p}{)}

\PY{n}{ax2}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta\PYZdl{} (GAIA DR2)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax2}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta\PYZdl{} (GAIA DR3)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{ylim} \PY{o}{=} \PY{n}{ax2}\PY{o}{.}\PY{n}{get\PYZus{}ylim}\PY{p}{(}\PY{p}{)}
\PY{n}{xlim} \PY{o}{=} \PY{n}{ax2}\PY{o}{.}\PY{n}{get\PYZus{}xlim}\PY{p}{(}\PY{p}{)}
\PY{n}{x}\PY{o}{=}\PY{n}{y}\PY{o}{=}\PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{o}{*}\PY{n}{ylim}\PY{p}{)}
\PY{n}{ax2}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{x}\PY{p}{,}\PY{n}{y}\PY{p}{,}\PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}\PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax2}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{n}{ylim}\PY{p}{)}
\PY{n}{ax2}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{n}{xlim}\PY{p}{)}

\PY{c+c1}{\PYZsh{} Then a histogram of the difference in the uncertainties}
\PY{n}{err\PYZus{}diff} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}error\PYZus{}dr3} \PY{o}{\PYZhy{}} \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}alpha\PYZus{}err\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}
\PY{n}{med} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmedian}\PY{p}{(}\PY{n}{err\PYZus{}diff}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{err\PYZus{}diff}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fill}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{Delta }\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{alpha,DR3\PYZcb{} \PYZhy{} }\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{Delta }\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{alpha,DR2\PYZcb{}\PYZdl{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{N}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{axvline}\PY{p}{(}\PY{n}{med}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax3}\PY{o}{.}\PY{n}{text}\PY{p}{(}\PY{n}{med}\PY{p}{,} \PY{l+m+mi}{5}\PY{p}{,} \PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Median=}\PY{l+s+si}{\PYZob{}}\PY{n}{med}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{rotation}\PY{o}{=}\PY{l+m+mi}{90}\PY{p}{,} \PY{n}{verticalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{horizontalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{backgroundcolor}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{white}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{err\PYZus{}diff} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}error\PYZus{}dr3} \PY{o}{\PYZhy{}} \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}delta\PYZus{}err\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}
\PY{n}{med} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmedian}\PY{p}{(}\PY{n}{err\PYZus{}diff}\PY{p}{)}
\PY{n}{ax4}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{err\PYZus{}diff}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fill}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
\PY{n}{ax4}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{Delta }\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta,DR3\PYZcb{} \PYZhy{} }\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{Delta }\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta,DR2\PYZcb{}\PYZdl{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax4}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{N}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax4}\PY{o}{.}\PY{n}{axvline}\PY{p}{(}\PY{n}{med}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax4}\PY{o}{.}\PY{n}{text}\PY{p}{(}\PY{n}{med}\PY{p}{,} \PY{l+m+mf}{6.5}\PY{p}{,} \PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Median=}\PY{l+s+si}{\PYZob{}}\PY{n}{med}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{rotation}\PY{o}{=}\PY{l+m+mi}{90}\PY{p}{,} \PY{n}{verticalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{horizontalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{backgroundcolor}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{white}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{c+c1}{\PYZsh{} then a histogram of the difference in the proper motion values}
\PY{n}{diff} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}dr3} \PY{o}{\PYZhy{}} \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}alpha\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}
\PY{n}{mean} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmean}\PY{p}{(}\PY{n}{diff}\PY{p}{)}
\PY{n}{std} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanstd}\PY{p}{(}\PY{n}{diff}\PY{p}{)}

\PY{n}{ax5}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{diff}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fill}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
\PY{n}{ax5}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{alpha,DR3\PYZcb{} \PYZhy{} }\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{alpha,DR2\PYZcb{}\PYZdl{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax5}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{N}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax5}\PY{o}{.}\PY{n}{axvline}\PY{p}{(}\PY{n}{mean}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax5}\PY{o}{.}\PY{n}{axvline}\PY{p}{(}\PY{n}{mean}\PY{o}{+}\PY{l+m+mi}{5}\PY{o}{*}\PY{n}{std}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{:}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax5}\PY{o}{.}\PY{n}{axvline}\PY{p}{(}\PY{n}{mean}\PY{o}{\PYZhy{}}\PY{l+m+mi}{5}\PY{o}{*}\PY{n}{std}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{:}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax5}\PY{o}{.}\PY{n}{text}\PY{p}{(}\PY{n}{mean}\PY{p}{,} \PY{l+m+mi}{5}\PY{p}{,} \PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Mean=}\PY{l+s+si}{\PYZob{}}\PY{n}{mean}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{rotation}\PY{o}{=}\PY{l+m+mi}{90}\PY{p}{,} \PY{n}{verticalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{horizontalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{backgroundcolor}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{white}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax5}\PY{o}{.}\PY{n}{text}\PY{p}{(}\PY{n}{mean}\PY{o}{+}\PY{l+m+mi}{5}\PY{o}{*}\PY{n}{std}\PY{p}{,} \PY{l+m+mi}{5}\PY{p}{,} \PY{l+s+sa}{rf}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}5}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{sigma\PYZdl{}=}\PY{l+s+si}{\PYZob{}}\PY{n}{std}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{rotation}\PY{o}{=}\PY{l+m+mi}{90}\PY{p}{,} \PY{n}{verticalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{horizontalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{backgroundcolor}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{white}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{diff} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}dr3} \PY{o}{\PYZhy{}} \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}delta\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}
\PY{n}{mean} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanmean}\PY{p}{(}\PY{n}{diff}\PY{p}{)}
\PY{n}{std} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{nanstd}\PY{p}{(}\PY{n}{diff}\PY{p}{)}

\PY{n}{ax6}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n}{diff}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{fill}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
\PY{n}{ax6}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta,DR3\PYZcb{} \PYZhy{} }\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta,DR2\PYZcb{}\PYZdl{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax6}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{N}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax6}\PY{o}{.}\PY{n}{axvline}\PY{p}{(}\PY{n}{mean}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax6}\PY{o}{.}\PY{n}{axvline}\PY{p}{(}\PY{n}{mean}\PY{o}{+}\PY{l+m+mi}{5}\PY{o}{*}\PY{n}{std}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{:}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax6}\PY{o}{.}\PY{n}{axvline}\PY{p}{(}\PY{n}{mean}\PY{o}{\PYZhy{}}\PY{l+m+mi}{5}\PY{o}{*}\PY{n}{std}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{:}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{ax6}\PY{o}{.}\PY{n}{text}\PY{p}{(}\PY{n}{mean}\PY{p}{,} \PY{l+m+mf}{6.5}\PY{p}{,} \PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Mean=}\PY{l+s+si}{\PYZob{}}\PY{n}{mean}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{rotation}\PY{o}{=}\PY{l+m+mi}{90}\PY{p}{,} \PY{n}{verticalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{horizontalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{backgroundcolor}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{white}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax6}\PY{o}{.}\PY{n}{text}\PY{p}{(}\PY{n}{mean}\PY{o}{+}\PY{l+m+mi}{5}\PY{o}{*}\PY{n}{std}\PY{p}{,} \PY{l+m+mf}{6.5}\PY{p}{,} \PY{l+s+sa}{rf}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}5}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{sigma\PYZdl{}=}\PY{l+s+si}{\PYZob{}}\PY{n}{std}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{rotation}\PY{o}{=}\PY{l+m+mi}{90}\PY{p}{,} \PY{n}{verticalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{horizontalalignment}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{center}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{backgroundcolor}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{white}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{6}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
Text(10.219034500144446, 6.5, '\$5\textbackslash{}\textbackslash{}sigma\$=2.11')
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Franz_ASTR540_HW4_NB_files/Franz_ASTR540_HW4_NB_8_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsubsection{Problem 1b Discussion}\label{problem-1b-discussion}

The median improvement in the uncertainties in proper motions is
\textasciitilde0.50 mas/yr. See the above histograms (row 2 in the above
plot) for the distribution of improvements. As shown in the third row of
the above plot, there have not been any \textgreater{} 5 changes in the
proper motion between gaia DR3 and DR2 for this small sample.

\subsubsection{Problem 1c}\label{problem-1c}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{7}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} compute the error weighted mean}
\PY{n}{pmra}\PY{p}{,} \PY{n}{pmra\PYZus{}wt} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}dr3}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}dr3}\PY{p}{)}\PY{p}{]}\PY{p}{,} \PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}error\PYZus{}dr3}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}dr3}\PY{p}{)}\PY{p}{]}
\PY{n}{pmdec}\PY{p}{,} \PY{n}{pmdec\PYZus{}wt} \PY{o}{=} \PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}dr3}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}dr3}\PY{p}{)}\PY{p}{]}\PY{p}{,} \PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}error\PYZus{}dr3}\PY{p}{[}\PY{o}{\PYZti{}}\PY{n}{pd}\PY{o}{.}\PY{n}{isna}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}dr3}\PY{p}{)}\PY{p}{]}

\PY{n}{where\PYZus{}not\PYZus{}outlier} \PY{o}{=} \PY{n}{pmra}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{cos}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{dec\PYZus{}dr3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{o}{/}\PY{l+m+mi}{180}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{o}{\PYZhy{}}\PY{l+m+mi}{4}
\PY{n}{pmra} \PY{o}{=} \PY{n}{pmra}\PY{p}{[}\PY{n}{where\PYZus{}not\PYZus{}outlier}\PY{p}{]}
\PY{n}{pmra\PYZus{}wt} \PY{o}{=} \PY{n}{pmra\PYZus{}wt}\PY{p}{[}\PY{n}{where\PYZus{}not\PYZus{}outlier}\PY{p}{]}
\PY{n}{pmdec} \PY{o}{=} \PY{n}{pmdec}\PY{p}{[}\PY{n}{where\PYZus{}not\PYZus{}outlier}\PY{p}{]}
\PY{n}{pmdec\PYZus{}wt} \PY{o}{=} \PY{n}{pmdec\PYZus{}wt}\PY{p}{[}\PY{n}{where\PYZus{}not\PYZus{}outlier}\PY{p}{]}

\PY{n}{mean\PYZus{}pmra} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{average}\PY{p}{(}\PY{n}{pmra}\PY{p}{,} \PY{n}{weights}\PY{o}{=}\PY{n}{pmra\PYZus{}wt}\PY{p}{)}
\PY{n}{std\PYZus{}pmra} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{average}\PY{p}{(}\PY{p}{(}\PY{n}{pmra}\PY{o}{\PYZhy{}}\PY{n}{mean\PYZus{}pmra}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{,} \PY{n}{weights}\PY{o}{=}\PY{n}{pmra\PYZus{}wt}\PY{p}{)}\PY{p}{)}

\PY{n}{mean\PYZus{}pmdec} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{average}\PY{p}{(}\PY{n}{pmdec}\PY{p}{,} \PY{n}{weights}\PY{o}{=}\PY{n}{pmdec\PYZus{}wt}\PY{p}{)}
\PY{n}{std\PYZus{}pmdec} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{average}\PY{p}{(}\PY{p}{(}\PY{n}{pmdec}\PY{o}{\PYZhy{}}\PY{n}{mean\PYZus{}pmdec}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{,} \PY{n}{weights}\PY{o}{=}\PY{n}{pmdec\PYZus{}wt}\PY{p}{)}\PY{p}{)}

\PY{n+nb}{print}\PY{p}{(}\PY{l+s+sa}{rf}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{(\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}a\PYZti{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{cos}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta\PYZdl{}, \PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta\PYZdl{}) = (}\PY{l+s+si}{\PYZob{}}\PY{n}{mean\PYZus{}pmra}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{, }\PY{l+s+si}{\PYZob{}}\PY{n}{mean\PYZus{}pmdec}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{) \PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{pm\PYZdl{} (}\PY{l+s+si}{\PYZob{}}\PY{n}{std\PYZus{}pmra}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{, }\PY{l+s+si}{\PYZob{}}\PY{n}{std\PYZus{}pmdec}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{c+c1}{\PYZsh{} make plot similar to Fig. 1 from the paper}

\PY{n}{fig}\PY{p}{,} \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplots}\PY{p}{(}\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}
    \PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}dr3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{cos}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{dec\PYZus{}dr3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{o}{/}\PY{l+m+mi}{180}\PY{p}{)}\PY{p}{,}
    \PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}dr3}\PY{p}{,}
    \PY{n}{xerr}\PY{o}{=}\PY{n}{data}\PY{o}{.}\PY{n}{pmra\PYZus{}error\PYZus{}dr3}\PY{p}{,}
    \PY{n}{yerr}\PY{o}{=}\PY{n}{data}\PY{o}{.}\PY{n}{pmdec\PYZus{}error\PYZus{}dr3}\PY{p}{,}
    \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{none}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{marker}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{o}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} 
    \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{GAIA DR3}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{cornflowerblue}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.5}
\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{errorbar}\PY{p}{(}
    \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}alpha\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{cos}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{delta\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{o}{/}\PY{l+m+mi}{180}\PY{p}{)}\PY{p}{,}
    \PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}delta\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{xerr}\PY{o}{=}\PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}alpha\PYZus{}err\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{yerr}\PY{o}{=}\PY{n}{data}\PY{o}{.}\PY{n}{mu\PYZus{}delta\PYZus{}err\PYZus{}dr2}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{none}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{marker}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{o}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{GAIA DR2}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firebrick}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{alpha}\PY{o}{=}\PY{l+m+mf}{0.5}
\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta\PYZdl{} [mas/yr]}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{mu\PYZus{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{alpha\PYZti{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{cos}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{delta\PYZdl{} [mas/yr]}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{8}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{8}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
(\$\textbackslash{}mu\_a\textasciitilde{}\textbackslash{}cos\textbackslash{}delta\$, \$\textbackslash{}mu\_\textbackslash{}delta\$) = (-1.39, -1.44) \$\textbackslash{}pm\$ (0.69, 0.92)
    \end{Verbatim}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{7}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
<matplotlib.legend.Legend at 0x7d2d117a41d0>
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Franz_ASTR540_HW4_NB_files/Franz_ASTR540_HW4_NB_10_2.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsubsection{Problem 1c Discussion}\label{problem-1c-discussion}

I get a mean proper motion, weighted by the uncertainties, of
(\(\mu_a~\cos\delta\), \(\mu_\delta\)) = (-1.39, -1.44) \(\pm\) (0.69,
0.92) from the Gaia DR3 dataset. This is consistent with the value from
Gaia DR2 within \(1\sigma\). Although, interestingly, the uncertainties
on the mean are much larger for DR3 than DR2. I'm not sure how it was
computed in the paper, but I did did a weighted standard deviation to
compute the statistical uncertainty.

\subsubsection{Problem 1d}\label{problem-1d}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{8}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{isofile} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{fehm20afem2.SDSSugriz}\PY{l+s+s2}{\PYZdq{}}
\PY{n}{boo3\PYZus{}distance} \PY{o}{=} \PY{l+m+mf}{46.5} \PY{c+c1}{\PYZsh{} kpc, from the paper}

\PY{k}{def} \PY{n+nf}{M\PYZus{}to\PYZus{}m}\PY{p}{(}\PY{n}{M}\PY{p}{,} \PY{n}{d}\PY{o}{=}\PY{n}{boo3\PYZus{}distance}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{M} \PY{o}{+} \PY{l+m+mi}{5}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{log10}\PY{p}{(}\PY{n}{d}\PY{o}{/}\PY{l+m+mi}{10}\PY{p}{)}

\PY{k}{with} \PY{n+nb}{open}\PY{p}{(}\PY{n}{isofile}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} \PY{k}{as} \PY{n}{f}\PY{p}{:}
    \PY{n}{iso\PYZus{}data} \PY{o}{=} \PY{n}{f}\PY{o}{.}\PY{n}{readlines}\PY{p}{(}\PY{p}{)}

\PY{n}{hdr} \PY{o}{=} \PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{:}\PY{l+m+mi}{6}\PY{p}{]}
\PY{n}{iso\PYZus{}data} \PY{o}{=} \PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{l+m+mi}{6}\PY{p}{:}\PY{p}{]}

\PY{n}{hdr\PYZus{}vals} \PY{o}{=} \PY{p}{[}\PY{n}{val}\PY{o}{.}\PY{n}{strip}\PY{p}{(}\PY{p}{)} \PY{k}{for} \PY{n}{val} \PY{o+ow}{in} \PY{n}{hdr}\PY{p}{[}\PY{l+m+mi}{3}\PY{p}{]}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ }\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} \PY{k}{if} \PY{n}{val} \PY{o+ow}{not} \PY{o+ow}{in} \PY{p}{\PYZob{}}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{\PYZcb{}}\PY{p}{]}
\PY{n}{mix\PYZus{}len}\PY{p}{,} \PY{n}{Y}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{Zeff}\PY{p}{,} \PY{n}{Fe\PYZus{}H}\PY{p}{,} \PY{n}{a\PYZus{}Fe} \PY{o}{=} \PY{n}{hdr\PYZus{}vals}

\PY{n}{isochrones\PYZus{}in\PYZus{}this\PYZus{}file} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\PY{n}{base\PYZus{}iso} \PY{o}{=} \PY{n+nb}{dict}\PY{p}{(}
    \PY{n}{idx} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{M} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{LogTeff} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{LogG} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{LogL} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{u} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{g} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{r} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{i} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{z} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{age} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{mix\PYZus{}len} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{Y} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{Z} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{Zeff} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{Fe\PYZus{}H} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
    \PY{n}{a\PYZus{}Fe} \PY{o}{=} \PY{p}{[}\PY{p}{]}\PY{p}{,}
\PY{p}{)}
\PY{n}{iso} \PY{o}{=} \PY{n}{deepcopy}\PY{p}{(}\PY{n}{base\PYZus{}iso}\PY{p}{)}
\PY{n}{age} \PY{o}{=} \PY{k+kc}{None}

\PY{k}{for} \PY{n}{j} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{iso\PYZus{}data}\PY{p}{)}\PY{p}{)}\PY{p}{:}
    \PY{k}{if} \PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{n}{j}\PY{p}{]} \PY{o}{==} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s1}{\PYZsq{}}\PY{p}{:}
        \PY{k}{continue}

    \PY{k}{if} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}AGE}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{in} \PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{n}{j}\PY{p}{]}\PY{p}{:}
        \PY{n}{isochrones\PYZus{}in\PYZus{}this\PYZus{}file}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{iso}\PY{p}{)}\PY{p}{)}

        \PY{n}{age} \PY{o}{=} \PY{n+nb}{float}\PY{p}{(}\PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{n}{j}\PY{p}{]}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ EEPS=}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{AGE=}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{strip}\PY{p}{(}\PY{p}{)}\PY{p}{)}
        \PY{n}{iso} \PY{o}{=} \PY{n}{deepcopy}\PY{p}{(}\PY{n}{base\PYZus{}iso}\PY{p}{)}
        \PY{k}{continue}

    \PY{k}{if} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZsh{}}\PY{l+s+s1}{\PYZsq{}} \PY{o}{==} \PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{n}{j}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{:}
        \PY{c+c1}{\PYZsh{} this line is a header}
        \PY{k}{continue}

    \PY{n}{line} \PY{o}{=} \PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{n}{j}\PY{p}{]}
    \PY{n}{goodline} \PY{o}{=} \PY{p}{[}\PY{n}{val} \PY{k}{for} \PY{n}{val} \PY{o+ow}{in} \PY{n}{line}\PY{o}{.}\PY{n}{strip}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ }\PY{l+s+s1}{\PYZsq{}}\PY{p}{)} \PY{k}{if} \PY{n+nb}{len}\PY{p}{(}\PY{n}{val}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{]}

    \PY{k}{if} \PY{n+nb}{len}\PY{p}{(}\PY{n}{goodline}\PY{p}{)} \PY{o}{!=} \PY{l+m+mi}{10}\PY{p}{:}
        \PY{n+nb}{print}\PY{p}{(}\PY{n}{goodline}\PY{p}{)}
        \PY{k}{continue}

    \PY{k}{for} \PY{n}{val}\PY{p}{,} \PY{n}{key} \PY{o+ow}{in} \PY{n+nb}{zip}\PY{p}{(}\PY{n}{goodline}\PY{p}{,} \PY{n}{iso}\PY{o}{.}\PY{n}{keys}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PY{p}{:}
        \PY{c+c1}{\PYZsh{} if key == \PYZsq{}age\PYZsq{}: continue}
        \PY{n}{iso}\PY{p}{[}\PY{n}{key}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{val}\PY{p}{)}

    \PY{n}{iso}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{age}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{age}\PY{p}{)}
    \PY{n}{iso}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{mix\PYZus{}len}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{mix\PYZus{}len}\PY{p}{)}
    \PY{n}{iso}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Y}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{Y}\PY{p}{)}
    \PY{n}{iso}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Z}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{Z}\PY{p}{)}
    \PY{n}{iso}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Zeff}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{Zeff}\PY{p}{)}
    \PY{n}{iso}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Fe\PYZus{}H}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{Fe\PYZus{}H}\PY{p}{)}
    \PY{n}{iso}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{a\PYZus{}Fe}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{a\PYZus{}Fe}\PY{p}{)}

\PY{n}{iso\PYZus{}data} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{concat}\PY{p}{(}\PY{n}{isochrones\PYZus{}in\PYZus{}this\PYZus{}file}\PY{p}{)}\PY{o}{.}\PY{n}{reset\PYZus{}index}\PY{p}{(}\PY{n}{drop}\PY{o}{=}\PY{k+kc}{True}\PY{p}{)}

\PY{c+c1}{\PYZsh{} select just the 10 Gyr one}
\PY{n}{iso\PYZus{}data} \PY{o}{=} \PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{age} \PY{o}{==} \PY{l+m+mi}{10}\PY{p}{]}

\PY{c+c1}{\PYZsh{} scale all of the magnitudes to boo3\PYZus{}distance}
\PY{k}{for} \PY{n}{filt} \PY{o+ow}{in} \PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{u}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{g}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{r}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{i}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{z}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{p}{:}
    \PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{n}{filt}\PY{p}{]} \PY{o}{=} \PY{n}{M\PYZus{}to\PYZus{}m}\PY{p}{(}\PY{n}{iso\PYZus{}data}\PY{p}{[}\PY{n}{filt}\PY{p}{]}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,} \PY{n}{d}\PY{o}{=}\PY{n}{boo3\PYZus{}distance}\PY{o}{*}\PY{l+m+mf}{1e3}\PY{p}{)}

\PY{n}{iso\PYZus{}data}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{8}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
      idx         M LogTeff    LogG     LogL          u          g          r  \textbackslash{}
7068   12  0.103511  3.5376  5.3748  -2.8181  36.404765  32.468665  30.781265
7069   13  0.113801  3.5502  5.3310  -2.6829  35.490765  31.976365  30.362465
7070   14  0.125317  3.5628  5.2860  -2.5455  34.679065  31.476965  29.948765
7071   15  0.138532  3.5743  5.2421  -2.4122  33.980765  30.999365  29.558465
7072   16  0.152713  3.5827  5.2041  -2.2982  33.447165  30.609265  29.235965
{\ldots}   {\ldots}       {\ldots}     {\ldots}     {\ldots}      {\ldots}        {\ldots}        {\ldots}        {\ldots}
7331  275  0.856466  3.6502  0.7935   3.1312  18.666965  16.462765  15.466865
7332  276  0.856473  3.6486  0.7629   3.1556  18.667265  16.425365  15.414365
7333  277  0.856479  3.6471  0.7331   3.1795  18.669365  16.389665  15.363365
7334  278  0.856486  3.6457  0.7042   3.2026  18.672265  16.355565  15.314365
7335  279  0.856491  3.6444  0.6775   3.2240  18.675365  16.324365  15.269265

              i          z   age mix\_len       Y           Z        Zeff  \textbackslash{}
7068  30.051865  29.662965  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
7069  29.705465  29.342965  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
7070  29.348765  29.010965  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
7071  29.001365  28.684265  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
7072  28.706265  28.403265  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
{\ldots}         {\ldots}        {\ldots}   {\ldots}     {\ldots}     {\ldots}         {\ldots}         {\ldots}
7331  15.087665  14.876465  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
7332  15.029165  14.814465  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
7333  14.972265  14.754065  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
7334  14.917465  14.695765  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04
7335  14.866865  14.641965  10.0  1.9380  0.2452  1.2990E-04  1.6990E-04

       Fe\_H   a\_Fe
7068  -2.01  -0.20
7069  -2.01  -0.20
7070  -2.01  -0.20
7071  -2.01  -0.20
7072  -2.01  -0.20
{\ldots}     {\ldots}    {\ldots}
7331  -2.01  -0.20
7332  -2.01  -0.20
7333  -2.01  -0.20
7334  -2.01  -0.20
7335  -2.01  -0.20

[268 rows x 17 columns]
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{9}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{boo3\PYZus{}distance} \PY{o}{=} \PY{l+m+mf}{46.5} \PY{c+c1}{\PYZsh{} kpc, from the paper}
\PY{n}{boo3\PYZus{}delta\PYZus{}distance} \PY{o}{=} \PY{l+m+mi}{2} \PY{c+c1}{\PYZsh{} kpc, the value used in the paper}
\PY{n}{boo3\PYZus{}radius} \PY{o}{=} \PY{l+m+mi}{30} \PY{c+c1}{\PYZsh{} arcmin, value used for the cone search in the paper}
\PY{n}{pmra\PYZus{}min}\PY{p}{,} \PY{n}{pmra\PYZus{}max} \PY{o}{=} \PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{3}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)} \PY{c+c1}{\PYZsh{} mu\PYZus{}alpha * cos(delta) in mas/yr}
\PY{n}{pmdec\PYZus{}min}\PY{p}{,} \PY{n}{pmdec\PYZus{}max} \PY{o}{=} \PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{3}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)} \PY{c+c1}{\PYZsh{} mu\PYZus{}delta in mas/yr}

\PY{c+c1}{\PYZsh{} Color\PYZhy{}magnitude filter: this requires stars to be within}
\PY{c+c1}{\PYZsh{} 0.1 mag at g0 = 16, increasing linearly to 0.2 mag width at g0 = 22.5}
\PY{k}{def} \PY{n+nf}{cmd\PYZus{}filter}\PY{p}{(}\PY{n}{g\PYZus{}mag}\PY{p}{)}\PY{p}{:}
    \PY{n}{p} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{polyfit}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{l+m+mi}{16}\PY{p}{,} \PY{l+m+mf}{22.5}\PY{p}{)}\PY{p}{,} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{l+m+mf}{0.1}\PY{p}{,}\PY{l+m+mf}{0.2}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}
    \PY{n}{cmd\PYZus{}filter} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{polyval}\PY{p}{(}\PY{n}{p}\PY{o}{=}\PY{n}{p}\PY{p}{,} \PY{n}{x}\PY{o}{=}\PY{n}{g\PYZus{}mag}\PY{p}{)}
    \PY{k}{return} \PY{n}{cmd\PYZus{}filter}

\PY{k}{def} \PY{n+nf}{is\PYZus{}within\PYZus{}cmd\PYZus{}filter}\PY{p}{(}\PY{n}{g\PYZus{}mag}\PY{p}{,} \PY{n}{r\PYZus{}mag}\PY{p}{,} \PY{n}{isochrone}\PY{p}{)}\PY{p}{:}
    \PY{n}{filt} \PY{o}{=} \PY{n}{cmd\PYZus{}filter}\PY{p}{(}\PY{n}{g\PYZus{}mag}\PY{p}{)}

    \PY{c+c1}{\PYZsh{} find closest isochrone point}
    \PY{c+c1}{\PYZsh{} good enough for now}
    \PY{n}{min\PYZus{}idx} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{argmin}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{abs}\PY{p}{(}\PY{n}{g\PYZus{}mag}\PY{o}{\PYZhy{}}\PY{n}{isochrone}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{values}\PY{p}{)}\PY{p}{)}
    \PY{n}{g}\PY{p}{,} \PY{n}{r} \PY{o}{=} \PY{n}{isochrone}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{values}\PY{p}{[}\PY{n}{min\PYZus{}idx}\PY{p}{]}\PY{p}{,} \PY{n}{isochrone}\PY{o}{.}\PY{n}{r}\PY{o}{.}\PY{n}{values}\PY{p}{[}\PY{n}{min\PYZus{}idx}\PY{p}{]}

    \PY{n}{color} \PY{o}{=} \PY{n}{g\PYZus{}mag} \PY{o}{\PYZhy{}} \PY{n}{r\PYZus{}mag}

    \PY{k}{return} \PY{n}{color} \PY{o}{\PYZlt{}}\PY{o}{=} \PY{p}{(}\PY{n}{g}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{+}\PY{n}{filt}\PY{p}{)} \PY{o+ow}{and} \PY{n}{color} \PY{o}{\PYZgt{}}\PY{o}{=} \PY{p}{(}\PY{n}{g}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{\PYZhy{}}\PY{n}{filt}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{10}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} first do a cone search in Gaia DR3}
\PY{n}{Gaia}\PY{o}{.}\PY{n}{ROW\PYZus{}LIMIT} \PY{o}{=} \PY{l+m+mi}{100\PYZus{}000}
\PY{n}{boo3\PYZus{}coord} \PY{o}{=} \PY{n}{SkyCoord}\PY{p}{(}\PY{l+m+mf}{209.3}\PY{p}{,} \PY{l+m+mf}{26.8}\PY{p}{,} \PY{n}{unit}\PY{o}{=}\PY{n}{u}\PY{o}{.}\PY{n}{deg}\PY{p}{)}
\PY{n}{res} \PY{o}{=} \PY{n}{Gaia}\PY{o}{.}\PY{n}{query\PYZus{}object}\PY{p}{(}
    \PY{n}{coordinate}\PY{o}{=}\PY{n}{boo3\PYZus{}coord}\PY{p}{,} 
    \PY{n}{radius}\PY{o}{=}\PY{n}{boo3\PYZus{}radius}\PY{o}{*}\PY{n}{u}\PY{o}{.}\PY{n}{arcmin}\PY{p}{,}
    \PY{n}{verbose}\PY{o}{=}\PY{k+kc}{False}
\PY{p}{)}

\PY{c+c1}{\PYZsh{} filter on proper motion}
\PY{n}{ra\PYZus{}res} \PY{o}{=} \PY{n}{res}\PY{p}{[}\PY{p}{(}\PY{n}{res}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{pmra}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{cos}\PY{p}{(}\PY{n}{res}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ra}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{to}\PY{p}{(}\PY{n}{u}\PY{o}{.}\PY{n}{radian}\PY{p}{)}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{n}{pmra\PYZus{}min}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{res}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{pmra}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{cos}\PY{p}{(}\PY{n}{res}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{ra}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{o}{.}\PY{n}{to}\PY{p}{(}\PY{n}{u}\PY{o}{.}\PY{n}{radian}\PY{p}{)}\PY{p}{)} \PY{o}{\PYZlt{}} \PY{n}{pmra\PYZus{}max}\PY{p}{)}\PY{p}{]}
\PY{n}{dec\PYZus{}res} \PY{o}{=} \PY{n}{ra\PYZus{}res}\PY{p}{[}\PY{p}{(}\PY{n}{ra\PYZus{}res}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{pmdec}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{\PYZgt{}} \PY{n}{pmdec\PYZus{}min}\PY{p}{)} \PY{o}{*} \PY{p}{(}\PY{n}{ra\PYZus{}res}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{pmdec}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{\PYZlt{}} \PY{n}{pmdec\PYZus{}max}\PY{p}{)}\PY{p}{]}

\PY{c+c1}{\PYZsh{} filter on the CMD cuts}
\PY{n}{res} \PY{o}{=} \PY{n}{get\PYZus{}sdss\PYZus{}colors}\PY{p}{(}\PY{n}{dec\PYZus{}res}\PY{o}{.}\PY{n}{to\PYZus{}pandas}\PY{p}{(}\PY{p}{)}\PY{p}{)}

\PY{n}{res}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{is\PYZus{}within\PYZus{}cmd\PYZus{}filter}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{n}{res}\PY{o}{.}\PY{n}{apply}\PY{p}{(}
    \PY{k}{lambda} \PY{n}{row} \PY{p}{:} \PY{n}{is\PYZus{}within\PYZus{}cmd\PYZus{}filter}\PY{p}{(}\PY{n}{row}\PY{o}{.}\PY{n}{g\PYZus{}sdss}\PY{p}{,} \PY{n}{row}\PY{o}{.}\PY{n}{r\PYZus{}sdss}\PY{p}{,} \PY{n}{iso\PYZus{}data}\PY{p}{)}\PY{p}{,}
    \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}
\PY{p}{)}

\PY{n}{res} \PY{o}{=} \PY{n}{res}\PY{p}{[}\PY{n}{res}\PY{o}{.}\PY{n}{is\PYZus{}within\PYZus{}cmd\PYZus{}filter}\PY{p}{]}

\PY{c+c1}{\PYZsh{} filter on g\PYZus{}0}
\PY{n}{res} \PY{o}{=} \PY{n}{res}\PY{p}{[}\PY{n}{res}\PY{o}{.}\PY{n}{g\PYZus{}sdss} \PY{o}{\PYZlt{}} \PY{l+m+mi}{20}\PY{p}{]}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
/tmp/ipykernel\_466903/2148086655.py:22: UserWarning: Skipping Gaia DR3
1450837238169921280 because no SDSS data!
  warnings.warn(f"Skipping \{row.DESIGNATION\} because no SDSS data!")
    \end{Verbatim}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{11}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} read in Table 2 from Carlin \PYZam{} Sand (2018)}
\PY{n}{dr2\PYZus{}res} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{read\PYZus{}csv}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Carlin\PYZus{}and\PYZus{}Sand\PYZus{}2018\PYZus{}Table2.txt}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{sep}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{dr2\PYZus{}res} \PY{o}{=} \PY{n}{get\PYZus{}sdss\PYZus{}colors}\PY{p}{(}\PY{n}{dr2\PYZus{}res}\PY{p}{,} \PY{n}{ra\PYZus{}key}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{alpha}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{dec\PYZus{}key}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{delta}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{c+c1}{\PYZsh{} then plot it up!}
\PY{n}{fig}\PY{p}{,} \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplots}\PY{p}{(}\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{r}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,} \PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{10 Gyr}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s2}{[Fe/H]=\PYZhy{}2}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{data}\PY{o}{.}\PY{n}{g\PYZus{}sdss}\PY{o}{\PYZhy{}}\PY{n}{data}\PY{o}{.}\PY{n}{r\PYZus{}sdss}\PY{p}{,} \PY{n}{data}\PY{o}{.}\PY{n}{g\PYZus{}sdss}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{o}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{none}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Original Data}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{res}\PY{o}{.}\PY{n}{g\PYZus{}sdss}\PY{o}{\PYZhy{}}\PY{n}{res}\PY{o}{.}\PY{n}{r\PYZus{}sdss}\PY{p}{,} \PY{n}{res}\PY{o}{.}\PY{n}{g\PYZus{}sdss}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{s}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{edgecolor}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{facecolor}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{none}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Gaia DR3 Search Results}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{scatter}\PY{p}{(}\PY{n}{dr2\PYZus{}res}\PY{o}{.}\PY{n}{g\PYZus{}sdss}\PY{o}{\PYZhy{}}\PY{n}{dr2\PYZus{}res}\PY{o}{.}\PY{n}{r\PYZus{}sdss}\PY{p}{,} \PY{n}{dr2\PYZus{}res}\PY{o}{.}\PY{n}{g\PYZus{}sdss}\PY{p}{,} \PY{n}{marker}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{X}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{edgecolor}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{facecolor}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{none}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Gaia DR2 Search Results}\PY{l+s+se}{\PYZbs{}n}\PY{l+s+s2}{Carlin \PYZam{} Sand (2018)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}
    \PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{r}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)} \PY{o}{+} \PY{n}{cmd\PYZus{}filter}\PY{p}{(}\PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{)}\PY{p}{,}
    \PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{label} \PY{o}{=} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CMD Filter Ranges}\PY{l+s+s2}{\PYZdq{}}
\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{plot}\PY{p}{(}
    \PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{r}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n}{cmd\PYZus{}filter}\PY{p}{(}\PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{)}\PY{p}{,}
    \PY{n}{iso\PYZus{}data}\PY{o}{.}\PY{n}{g}\PY{o}{.}\PY{n}{astype}\PY{p}{(}\PY{n+nb}{float}\PY{p}{)}\PY{p}{,}
    \PY{n}{linestyle}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZhy{}\PYZhy{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{k}\PY{l+s+s1}{\PYZsq{}}
\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{invert\PYZus{}yaxis}\PY{p}{(}\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{g\PYZhy{}r}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{g}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{fontsize}\PY{o}{=}\PY{l+m+mi}{10}\PY{p}{)}

\PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}ylim}\PY{p}{(}\PY{l+m+mi}{22}\PY{p}{,} \PY{l+m+mi}{16}\PY{p}{)}
\PY{n}{ax}\PY{o}{.}\PY{n}{set\PYZus{}xlim}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mf}{0.8}\PY{p}{,} \PY{l+m+mf}{1.8}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{11}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
(-0.8, 1.8)
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{Franz_ASTR540_HW4_NB_files/Franz_ASTR540_HW4_NB_15_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsubsection{Problem 1d Discussion}\label{problem-1d-discussion}

We used the same proper motion filter, same color-magnitude diagram
filter, and maximum \(g < 20\) from Carlin \& Sand (2018) to search for
plausible main sequence and red giant branch proper motion members of
Bootes III. The results are shown in the figure above.

From the SDSS colors and Isochrones (from HW 1), we find 7 new proper
motion members of Bootes III. The Isochrone shown is for a 10 Gyr
cluster with a metallicity \([Fe/H]=-2\). Note that we do not find some
of the original members from Carlin \& Sand (2018) for two primary
reasons:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  We use SDSS magnitudes instead of Panstarrs magnitudes. This is
  because the Isochrone we have access to is for SDSS magnitudes. This
  changes the exact width of the Color Magnitude Diagram filter and
  eliminates some of them.
\item
  The Isochrone we are using does not include the population of bluer
  stars on the right side of the color-magnitude diagram. This is a
  limitation of this analysis.
\end{enumerate}

Additionally, it is important to note that these are simply
\textbf{plausible} members of Bootes III that need true RV measurements
to confirm. As described in Carlin \& Sand (2018), there are numerous
sources of contaminants for these proper motion calculations.

    \subsection{Problem 2}\label{problem-2}

Congratulations! You have discovered a dwarf galaxy around the Milky
Way. Wishing to refine it's distance, you took time series imaging data
of this new system and identified 3 RR Lyrae stars, whose proper- ties
are in the data file ``rrl.dat''. Infer the distance to the new dwarf
galaxy using the basic relations in Caceres \& Catelan 2008, ApJSS, 179,
242. You can assume a metallicity of Z=0.0001, but assume a 10\%
uncertainty on this value. For the average i and z band magnitudes, you
can assume 0.03 mag uncertainties, and a 0.01 day uncertainty on the RRL
periods. What is the distance (with uncertainty) to your newly
discovered dwarf galaxy?

The relevant equations in Caceres \& CAtelan (2008) are equations (6)
and (7):

\(M_z = 0.839 - 1.295~\log P + 0.211~\log Z\)

\(M_i = 0.908 - 1.035~\log P + 0.220~\log Z\)

Which has the general form
\(M_f = \gamma - \alpha~\log P + \beta~\log Z\)

From these we can use the distance modulus equation to find the distance
to each RR Lyrae Star

\(m - M = 5\log d - 5 \rightarrow \log d = \frac{m - M + 5}{5}\)

Substituting in the general formulation of M

\(\log d_f = \frac{1}{5} \left[ m_f - \gamma + \alpha~\log P - \beta~\log Z + 5 \right]\)

Which then, propagating uncertainty, has an uncertainty of

\(\sigma_d = d_f \left[\left(\alpha\frac{\sigma_P}{\ln(10)~ P}\right)^2 + \left(\beta\frac{\sigma_Z}{\ln(10)~Z}\right)^2 + \left(\frac{\sigma_m}{m_f}\right)^2 \right]^{1/2}\)

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{12}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{log\PYZus{}distance}\PY{p}{(}\PY{n}{P}\PY{p}{,} \PY{n}{sigma\PYZus{}P}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{sigma\PYZus{}Z}\PY{p}{,} \PY{n}{m}\PY{p}{,} \PY{n}{sigma\PYZus{}m}\PY{p}{,} \PY{n}{alpha}\PY{p}{,} \PY{n}{beta}\PY{p}{,} \PY{n}{gamma}\PY{p}{)}\PY{p}{:}
    \PY{n}{log\PYZus{}d} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{5} \PY{o}{*} \PY{p}{(}\PY{n}{m} \PY{o}{\PYZhy{}} \PY{n}{gamma} \PY{o}{+} \PY{n}{alpha}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{log10}\PY{p}{(}\PY{n}{P}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n}{beta}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{log10}\PY{p}{(}\PY{n}{Z}\PY{p}{)} \PY{o}{+} \PY{l+m+mi}{5}\PY{p}{)}
    \PY{n}{sigma\PYZus{}d} \PY{o}{=} \PY{n}{log\PYZus{}d} \PY{o}{*} \PY{p}{(} \PY{p}{(}\PY{n}{alpha}\PY{o}{*}\PY{n}{sigma\PYZus{}P}\PY{o}{/}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{l+m+mi}{10}\PY{p}{)}\PY{o}{*}\PY{n}{P}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2} \PY{o}{+} \PY{p}{(}\PY{n}{beta}\PY{o}{*}\PY{n}{sigma\PYZus{}Z}\PY{o}{/}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{l+m+mi}{10}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2} \PY{o}{+} \PY{p}{(}\PY{n}{sigma\PYZus{}m}\PY{o}{/}\PY{n}{m}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2} \PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mf}{0.5}

    \PY{k}{return} \PY{n}{log\PYZus{}d}\PY{p}{,} \PY{n}{sigma\PYZus{}d}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{13}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{rr\PYZus{}lyrae} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{read\PYZus{}csv}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{rrl.dat}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{sep}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ }\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}

\PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Z}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{l+m+mf}{0.0001}
\PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Z\PYZus{}err}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{l+m+mf}{0.1}\PY{o}{*}\PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{Z}

\PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{i\PYZus{}mag\PYZus{}err}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{l+m+mf}{0.03}
\PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{z\PYZus{}mag\PYZus{}err}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{l+m+mf}{0.03}

\PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Period\PYZus{}err}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]} \PY{o}{=} \PY{l+m+mf}{0.01}

\PY{n}{i\PYZus{}band\PYZus{}kwargs} \PY{o}{=} \PY{n+nb}{dict}\PY{p}{(}
    \PY{n}{alpha} \PY{o}{=} \PY{l+m+mf}{1.035}\PY{p}{,}
    \PY{n}{beta} \PY{o}{=} \PY{o}{\PYZhy{}}\PY{l+m+mf}{0.220}\PY{p}{,}
    \PY{n}{gamma} \PY{o}{=} \PY{l+m+mf}{0.908}
\PY{p}{)}

\PY{n}{z\PYZus{}band\PYZus{}kwargs} \PY{o}{=} \PY{n+nb}{dict}\PY{p}{(}
    \PY{n}{alpha} \PY{o}{=} \PY{l+m+mf}{1.295}\PY{p}{,}
    \PY{n}{beta} \PY{o}{=} \PY{o}{\PYZhy{}}\PY{l+m+mf}{0.211}\PY{p}{,}
    \PY{n}{gamma} \PY{o}{=} \PY{l+m+mf}{0.839}
\PY{p}{)}

\PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{log\PYZus{}d\PYZus{}i}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{log\PYZus{}d\PYZus{}i\PYZus{}err}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{log\PYZus{}distance}\PY{p}{(}
    \PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Period(d)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{Period\PYZus{}err}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{Z}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{Z\PYZus{}err}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{i\PYZus{}mag}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{i\PYZus{}mag\PYZus{}err}\PY{p}{,}
    \PY{o}{*}\PY{o}{*}\PY{n}{i\PYZus{}band\PYZus{}kwargs}
\PY{p}{)}

\PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{log\PYZus{}d\PYZus{}z}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{log\PYZus{}d\PYZus{}z\PYZus{}err}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{log\PYZus{}distance}\PY{p}{(}
    \PY{n}{rr\PYZus{}lyrae}\PY{p}{[}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Period(d)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{]}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{Period\PYZus{}err}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{Z}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{Z\PYZus{}err}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{z\PYZus{}mag}\PY{p}{,}
    \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{z\PYZus{}mag\PYZus{}err}\PY{p}{,}
    \PY{o}{*}\PY{o}{*}\PY{n}{z\PYZus{}band\PYZus{}kwargs}
\PY{p}{)}

\PY{n}{rr\PYZus{}lyrae}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{13}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
   Name     RA(deg)   DEC(deg)  Period(d)  i\_mag  z\_mag    A\_i    A\_z       Z  \textbackslash{}
0  RRL1  189.570323 -40.939879   0.389918  20.92  20.86  0.192  0.146  0.0001
1  RRL2  189.633635 -40.878072   0.422481  20.88  20.83  0.203  0.155  0.0001
2  RRL3  189.584351 -41.101214   0.735898  20.67  20.59  0.177  0.135  0.0001

     Z\_err  i\_mag\_err  z\_mag\_err  Period\_err   log\_d\_i  log\_d\_i\_err   log\_d\_z  \textbackslash{}
0  0.00001       0.03       0.03        0.01  4.741731     0.071321  4.729462
1  0.00001       0.03       0.03        0.01  4.740942     0.068136  4.732484
2  0.00001       0.03       0.03        0.01  4.748831     0.054291  4.746906

   log\_d\_z\_err
0     0.081105
1     0.076786
2     0.057062
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{14}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{print\PYZus{}results}\PY{p}{(}\PY{n}{log\PYZus{}dist}\PY{p}{,} \PY{n}{log\PYZus{}dist\PYZus{}err}\PY{p}{,} \PY{n}{varname}\PY{p}{)}\PY{p}{:}

    \PY{n}{dist} \PY{o}{=} \PY{l+m+mi}{10}\PY{o}{*}\PY{o}{*}\PY{n}{log\PYZus{}dist}
    \PY{n}{dist\PYZus{}err} \PY{o}{=} \PY{n}{log\PYZus{}dist\PYZus{}err} \PY{o}{*} \PY{n}{dist}\PY{o}{/}\PY{n}{log\PYZus{}dist}

    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+sa}{fr}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{\PYZdl{}}\PY{l+s+si}{\PYZob{}}\PY{n}{varname}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{\PYZdl{} = }\PY{l+s+si}{\PYZob{}}\PY{n}{dist}\PY{o}{/}\PY{l+m+mf}{1e3}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{ \PYZdl{}}\PY{l+s+s2}{\PYZbs{}}\PY{l+s+s2}{pm\PYZdl{} }\PY{l+s+si}{\PYZob{}}\PY{n}{dist\PYZus{}err}\PY{o}{/}\PY{l+m+mf}{1e3}\PY{l+s+si}{:}\PY{l+s+s2}{.2f}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{ kpc}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

\PY{n}{print\PYZus{}results}\PY{p}{(}\PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{log\PYZus{}d\PYZus{}z}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{log\PYZus{}d\PYZus{}z\PYZus{}err}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{d\PYZus{}z}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{print\PYZus{}results}\PY{p}{(}\PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{log\PYZus{}d\PYZus{}i}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{rr\PYZus{}lyrae}\PY{o}{.}\PY{n}{log\PYZus{}d\PYZus{}i\PYZus{}err}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{d\PYZus{}i}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
\$d\_z\$ = 54.49 \$\textbackslash{}pm\$ 0.82 kpc
\$d\_i\$ = 55.44 \$\textbackslash{}pm\$ 0.75 kpc
    \end{Verbatim}

    \subsubsection{Problem 2 Discussion}\label{problem-2-discussion}

The full results of the distance calculations for these three RR Lyrae
stars are shown in the table above. Since I compute the distance in both
z-band and i-band independently, we get two measurements of the
distance. These measurements, which I get by averaging the log distance
results, are consistent within uncertainties and give a distance of
\(d\sim (55\pm1) kpc\).

    \subsection{Problem 3}\label{problem-3}

Black Hole Accretion Time Scales As a mass m of gas falls into a black
hole, at most 0.1mc2 is likely to emerge as radiation; the rest is
swallowed by the black hole. Show that the Eddington luminosity for a
black hole of mass M is equivalent to 2×10−9 M c2 yr−1. Explain why we
expect the black hole's mass to grow by at least a factor of e every 5 ×
107 years.

We start by deriving the eddington luminosity in a typical way

\begin{equation}
F_g = F_{rad}
\end{equation}

\begin{equation}
\frac{G M m_p}{r^2} = \frac{ \sigma_T L_{edd} }{ 4 \pi c r^2 }
\end{equation}

Solving for \(L_{edd}\)

\begin{equation}
L_{edd} = \frac{4\pi G m_p}{c \sigma_T} Mc^2$
\end{equation}

Or in terms of years

\begin{equation}
L_{edd} = \frac{1.261\times10^8 \pi G m_p}{c \sigma_T} \frac{M c^2}{yr}
\end{equation}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{17}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{sec\PYZus{}to\PYZus{}year} \PY{o}{=} \PY{l+m+mi}{3600} \PY{o}{*} \PY{l+m+mi}{24} \PY{o}{*} \PY{l+m+mi}{365} \PY{o}{*} \PY{n}{u}\PY{o}{.}\PY{n}{s} \PY{o}{/} \PY{n}{u}\PY{o}{.}\PY{n}{yr}
\PY{c+c1}{\PYZsh{} print(f\PYZdq{}\PYZob{}sec\PYZus{}to\PYZus{}year*4:.2e\PYZcb{}\PYZdq{})}

\PY{n}{res\PYZus{}factor} \PY{o}{=} \PY{l+m+mi}{4}\PY{o}{*}\PY{n}{sec\PYZus{}to\PYZus{}year} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{pi} \PY{o}{*} \PY{n}{c}\PY{o}{.}\PY{n}{G} \PY{o}{*} \PY{n}{c}\PY{o}{.}\PY{n}{m\PYZus{}p} \PY{o}{/} \PY{p}{(}\PY{n}{c}\PY{o}{.}\PY{n}{c} \PY{o}{*} \PY{n}{c}\PY{o}{.}\PY{n}{sigma\PYZus{}T}\PY{p}{)}
\PY{n}{res\PYZus{}factor}
\end{Verbatim}
\end{tcolorbox}

\prompt{Out}{outcolor}{17}{}

    $2.2182837 \times 10^{-9} \; \mathrm{\frac{1}{yr}}$

    Using the above calculations

\begin{equation}
L_{edd} = 2.22\times10^{-9} Mc^2 yr^{-1}$
\end{equation}

We can also write a mass accretion rate

\begin{equation}
\dot{M}_{edd} = \frac{L_{edd}}{\epsilon c^2} = \frac{2.22\times10^{-9} M}{\epsilon} yr^{-1}
\end{equation}

We are given \(\epsilon = 0.1\) in the problem giving an equation

\begin{equation}
\dot{M}_{edd} = 2.22\times10^{-8} M yr^{-1}
\end{equation}

Integrating the mass from \(M_0 \rightarrow eM_0\) and from
\(t=0 \rightarrow t=\tau\) for an e-folding time \(\tau\) gives

\begin{equation}
\int_{M_0}^{e M_0} \dot{M}_{edd} dM = 2.22\times10^{-8}  yr^{-1} \int^{\tau}_{0} M dt
\end{equation}

Assuming an exponential growth from \(M_0 \rightarrow eM_0\) then we
have a functional form \(M = M_0 e^{t/\tau}\)

\begin{equation}
M_0 (e-1) = 2.22\times10^{-8}  M_0 yr^{-1} \int^{\tau}_{0} e^{t/\tau} dt
\end{equation}

\begin{equation}
M_0 (e-1) = 2.22\times10^{-8} M_0 yr^{-1} \tau (e - 1)
\end{equation}

Simplifying gives a timescale

\begin{equation}
\tau = \frac{yr}{2.22\times10^{-8}} = 4.5\times10^7 yr
\end{equation}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{16}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+si}{\PYZob{}}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mf}{2.22e\PYZhy{}8}\PY{p}{)}\PY{l+s+si}{:}\PY{l+s+s2}{.2e}\PY{l+s+si}{\PYZcb{}}\PY{l+s+s2}{ yr}\PY{l+s+s2}{\PYZdq{}}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{16}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
'4.50e+07 yr'
\end{Verbatim}
\end{tcolorbox}

    \subsection{Problem 4}\label{problem-4}

Closed Box Enrichment In a scenario where stars are made from gas that
is initially free of metals, so Z(t=0)=0, what is the mean metal
abundance of stars once all of the gas is gone?

\textbf{My Solution}

The average stellar metalicity is defined as

\begin{equation}
<z_s> = \frac{M_z}{M_s}
\end{equation}

Where \(M_z\) is the mass of the metals and \(M_s\) is the stellar mass.
At some time t, when \(M_g = 0\) (ie all the gas was used up to make
stars), we know that \(M_{tot} = M_s\) giving

\begin{equation}
<z_s> = \frac{M_z}{M_s}
\end{equation}

For an outer shell on the star \(\delta M_s\),

\begin{equation}
M_z = \int_0^t z(t) \delta M_s
\end{equation}

Changing variables to \(M_g\)

\begin{equation}
M_z = -\int_{M_{tot}}^0 z(M_g) \delta M_g
\end{equation}

Using the equation for \(z(M_g)\) derived in class gives an integral

\begin{equation}
M_z = P \int_{M_{tot}}^0 \ln\left(\frac{M_g}{M_{tot}}\right) \delta M_g
\end{equation}

\begin{equation}
M_z = P \left[ M_g \left( \ln\frac{M_g}{M_{tot}} - 1 \right) \right]^0_{M_{tot}}
\end{equation}

\begin{equation}
M_z = P \left[ 0 + M_g\right]
\end{equation}

\begin{equation}
M_z = P ~ M_g 
\end{equation}

Substituting this back into the equation for \(<z_s>\) gives

\begin{equation}
\boxed{<z_s> = P}
\end{equation}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]

\end{Verbatim}
\end{tcolorbox}

    % Add a bibliography block to the postdoc

\end{document}

### 2024-12-12 ASTR518/project/analysis/util.py
keep working on project analysis

@@ -1,0 +1,168 @@
+"""
+Some helpful utility code for the reduction and reduction analysis
+"""
+
+import os
+import glob
+
+from dataclasses import dataclass
+from collections.abc import MutableMapping
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+import ccdproc as ccdp
+
+from astropy.nddata import CCDData
+from astropy.visualization import hist
+from astropy.stats import mad_std
+from astropy import units as u
+
+ccdp_combine_kwargs = dict(
+    method="average",
+    sigma_clip=True,
+    sigma_clip_low_thresh=5,
+    sigma_clip_high_thresh=5,
+    sigma_clip_func=np.ma.median,
+    sigma_clip_dev_func=mad_std
+)
+
+class Kuiper:
+
+    # "static" variables
+    gain = 3.1 * u.electron/u.adu
+    electron_to_photons:u.Quantity = 1 *u.photon/u.electron
+        
+    def __init__(self, aperture_radius:int=5):
+        self.aperture_radius = aperture_radius
+        self.npix = np.pi*aperture_radius**2
+    
+class CustomCCDData(CCDData):
+    
+    def show_image(self, ax=None, fig=None, **kwargs):
+        
+        if ax is None:
+            fig, ax = plt.subplots()
+            
+        cmap = ax.imshow(self.data, cmap="gray", **kwargs)
+        
+        fig.colorbar(cmap)
+        
+        #ax.set_yticklabels([])
+        #ax.set_xticklabels([])
+            
+        return fig, ax
+
+@dataclass
+class ReductionFileSet:
+    file_list:str
+    filter_name:str
+
+class ReductionFileList(MutableMapping):
+    
+    def __init__(self, file_list:list[ReductionFileSet]):
+         self.__dict__ = {
+             file.filter_name:file.file_list for file in file_list
+         }
+    
+    def __setitem__(self, filter_name, file_list):
+        self.__dict__[filter_name] = file_list
+    
+    def __getitem__(self, filter_name):
+        return self.__dict__[filter_name]
+    
+    def __delitem__(self, filter_name):
+        del self.__dict__[filter_name]
+    
+    def __iter__(self):
+        return iter(self.__dict__)
+    
+    def __len__(self):
+        return len(self.__dict__)
+    
+    @staticmethod
+    def from_list(file_list, filter_names=None):
+        if filter_names is None:
+            return ReductionFileList([ReductionFileSet(file_list, "none")])
+        
+        # note this organization algorithm won't work for more complex 
[…]

### 2024-12-12 ASTR518/project/util.py

@@ -1,158 +1,0 @@
-"""
-Some helpful utility code for the reduction and reduction analysis
-"""
-
-import os
-import glob
-
-from dataclasses import dataclass
-from collections.abc import MutableMapping
-
-import numpy as np
-import matplotlib.pyplot as plt
-
-import ccdproc as ccdp
-
-from astropy.nddata import CCDData
-from astropy.visualization import hist
-from astropy.stats import mad_std
-from astropy import units as u
-
-ccdp_combine_kwargs = dict(
-    method="average",
-    sigma_clip=True,
-    sigma_clip_low_thresh=5,
-    sigma_clip_high_thresh=5,
-    sigma_clip_func=np.ma.median,
-    sigma_clip_dev_func=mad_std
-)
-
-class CustomCCDData(CCDData):
-    
-    def show_image(self, ax=None, fig=None, **kwargs):
-        
-        if ax is None:
-            fig, ax = plt.subplots()
-            
-        cmap = ax.imshow(self.data, cmap="gray", **kwargs)
-        
-        fig.colorbar(cmap)
-        
-        #ax.set_yticklabels([])
-        #ax.set_xticklabels([])
-            
-        return fig, ax
-
-@dataclass
-class ReductionFileSet:
-    file_list:str
-    filter_name:str
-
-class ReductionFileList(MutableMapping):
-    
-    def __init__(self, file_list:list[ReductionFileSet]):
-         self.__dict__ = {
-             file.filter_name:file.file_list for file in file_list
-         }
-    
-    def __setitem__(self, filter_name, file_list):
-        self.__dict__[filter_name] = file_list
-    
-    def __getitem__(self, filter_name):
-        return self.__dict__[filter_name]
-    
-    def __delitem__(self, filter_name):
-        del self.__dict__[filter_name]
-    
-    def __iter__(self):
-        return iter(self.__dict__)
-    
-    def __len__(self):
-        return len(self.__dict__)
-    
-    @staticmethod
-    def from_list(file_list, filter_names=None):
-        if filter_names is None:
-            return ReductionFileList([ReductionFileSet(file_list, "none")])
-        
-        # note this organization algorithm won't work for more complex 
-        # data directories but I'll simplify it here
-        return ReductionFileList([
-            ReductionFileSet(
-                file_list=[file for file in file_list if filt in os.path.basename(file)],
-                filter_name=filt
-            ) for filt in filter_names
-        ])
-        
[…]

### 2024-12-13 ASTR518/project/analysis/util.py
finish reducing the data and converting to mags

@@ -31,12 +31,12 @@ class Kuiper:
 
     # "static" variables
     gain = 3.1 * u.electron/u.adu
-    electron_to_photons:u.Quantity = 1 *u.photon/u.electron
-        
+    throughput = 0.8578 # assumed from Bok
+    quantum_efficiency = 0.7 # assumed from QE curve
     def __init__(self, aperture_radius:int=5):
         self.aperture_radius = aperture_radius
         self.npix = np.pi*aperture_radius**2
-    
+        self.electron_to_photons = 1/(self.throughput*self.quantum_efficiency)
 class CustomCCDData(CCDData):
     
     def show_image(self, ax=None, fig=None, **kwargs):
@@ -166,3 +166,35 @@ def single_flat_calib_and_combine(files, filter_name, combined_darks, exptime):
     )
     
     return combined_flat
+
+# this list is modified from the OTTER code I've written to find data for transients
+# https://github.com/astro-otter/otter/blob/main/src/otter/util.py#L731
+VIZIER_LARGE_CATALOGS = [
+    "AC2000.2",
+    "AKARI",
+    "ASCC-2.5",
+    "B/DENIS",
+    "CMC14",
+    "Gaia-DR1",
+    "GLIMPSE",
+    "GSC-ACT",
+    "GSC1.2",
+    "GSC2.2",
+    "GSC2.3",
+    "HIP",
+    "HIP2",
+    "IRAS",
+    "NOMAD1",
+    "PanSTARRS-DR1",
+    "PGC",
+    "Planck-DR1",
+    "PPMX",
+    "PPMXL",
+    "SDSS-DR12",
+    "SDSS-DR7",
+    "SDSS-DR9",
+    "Tycho-2",
+    "UKIDSS",
+    "USNO-A2",
+    "USNO-B1",
+]

### 2024-12-13 ASTR518/project/paper/main.tex
some more analysis plots and start filling in tables and plots in the paper

% Preamble
\documentclass{aastex631}

% imported packages
\usepackage{graphicx}

% reset commands to set the line spacing
\renewcommand{\baselinestretch}{1.5}

\begin{document}

\title{The Temporal Evolution of the Tidal Disruption Event AT2024wsd}

\author[0000-0003-4537-3575]{Noah Franz}
\affiliation{Department of Astronomy \& Steward Observatory, University of Arizona}

\begin{abstract}
  This is an abstract
\end{abstract}

\section{Introduction}

\section{Methods}
\subsection{Kuiper 61'' Observations}
\subsection{Data Calibration}

\subsection{Signal Extraction and Flux Calibration}

\begin{figure}
  \includegraphics[width=\textwidth]{../analysis/aperture-counts-hist.png}
  \caption{Caption}
  \label{fig:aperture-counts}
\end{figure}

\begin{figure}
  \includegraphics[width=\textwidth]{../analysis/target-images.png}
  \caption{Caption}
  \label{fig:targ}
\end{figure}

% \begin{figure}
%   \includegraphics[width=\textwidth]{../analysis/fcal-images.png}
%   \caption{Caption}
%   \label{fig:fcal}
% \end{figure}

\subsection{SED Modeling}

\section{Results}
\subsection{Observational Results}

\begin{table}
\caption{Reduction Results}
\label{tab:res}
\begin{tabular}{lllll}
Filter & Harris-V & Bessell-U & Harris-B & Harris-R \\
Source Aperture Sum (ADU) & 525131.38 & 95118.46 & 352222.45 & 554880.18 \\
Source Aperture Sum (e) & 1627907.28 & 294867.23 & 1091889.60 & 1720128.57 \\
Source Aperture Sum ($\gamma$) & 2711100.28 & 491068.91 & 1818421.88 & 2864684.69 \\
Background Annulus Sum (ADU) & 521430.41 & 94325.44 & 348674.99 & 549048.02 \\
Background Annulus Sum (e) & 1616434.28 & 292408.86 & 1080892.45 & 1702048.85 \\
Background Annulus Sum ($\gamma$) & 2691993.26 & 486974.75 & 1800107.34 & 2834574.90 \\
Dark Noise ($\sigma_D$; ADU) & 0.29 & 0.29 & 0.29 & 0.29 \\
Dark Noise ($\sigma_D$; e) & 0.51 & 0.51 & 0.51 & 0.51 \\
Read Noise ($\sigma_R$; ADU) & 3.26 & 3.26 & 3.26 & 3.26 \\
Read Noise ($\sigma_R$; e) & 10.10 & 10.10 & 10.10 & 10.10 \\
Signal ($f_e$; e) & 11473.00 & 2458.37 & 10997.15 & 18079.72 \\
Signal ($f_\gamma$; $\gamma$) & 19107.02 & 4094.15 & 18314.54 & 30109.79 \\
SNR & 8.74 & 3.94 & 10.10 & 13.42 \\
Zero Point ($10^{12}f_0$; $\gamma$) & 0.47 & 0.05 & 0.33 & 0.44 \\
Apparent Magnitude & 18.48 & 17.72 & 18.14 & 17.92 \\
Apparent Magnitude Error & 2.11 & 4.49 & 1.80 & 1.34 \\
\end{tabular}
\end{table}

This is where things like SNR and extracted magnitudes will go

\subsection{Modeling Results}

\section{Conclusions}

\end{document}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:

### 2024-12-15 ASTR518/project/analysis/util.py
finish analysis and work on writing

@@ -149,15 +149,23 @@ def single_dark_calib_stack(exptime_key, files, combined_bias):
     
     return combined_dark
 
-def single_flat_calib_and_combine(files, filter_name, combined_darks, exptime):
+def single_flat_calib_and_combine(files, filter_name, combined_darks, combined_bias, exptime):
+
+    flats_bias_calib = [
+        ccdp.subtract_bias(
+            CustomCCDData.read(file), 
+            combined_bias
+        ) 
+        for file in files.flat_files[filter_name]
+    ]
     
     flats_calib = [
         ccdp.subtract_dark(
-            CustomCCDData.read(file), 
+            data, 
             combined_darks, 
             dark_exposure=exptime, 
             data_exposure=exptime,
-        ) for file in files.flat_files[filter_name]
+        ) for data in flats_bias_calib
     ]
     
     combined_flat = ccdp.combine(

### 2024-12-15 ASTR518/project/paper/main.tex
finish second draft of paper

@@
-% Preamble
+% preamble
 \documentclass{aastex631}
@@
 \usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{natbib}
 
@@
 
-\title{The Temporal Evolution of the Tidal Disruption Event AT2024wsd}
+\title{Using Kuiper Observations to Explore the Temporal Evolution of the Tidal Disruption Event AT2024wsd}
 
-\author[0000-0003-4537-3575]{Noah Franz}
+\author[0000-0003-4537-3575]{noah franz}
 \affiliation{Department of Astronomy \& Steward Observatory, University of Arizona}
@@
 \begin{abstract}
-  This is an abstract
+  Tidal disruption events (TDEs) occur when a star is torn apart by the tidal forces of a supermassive black hole.
+This event produces emission across the electromagnetic spectrum that varies on the timescales of months to years, depending on the wavelength of the emission.
+The origin of much of this emission is unknown.
+With the recent advent of all sky optical surveys, most TDEs have been discovered and followed up in the optical wavelengths, providing detailed light curves with temporal sampling on the order of days.
+However, to distinguish between potential optical emission models, it is essential to obtain a well sampled peak of the emission light curve.
+As a result, in this work we observe the TDE AT2024wsd with the Kuiper 61'' telescope located on Mt.
+Graham near optical peak, the first work to use this telescope for TDE followup.
+We find that our data has a relatively high signal-to-noise ratio of $\sim4-10$, depending on the filter, with only a 50s exposure time.
+From this data, we are also able to poorly constrain the rise rate of the system to be $\sim -0.05$ mag/day.
+This proof of concept study demonstrates that the Kuiper 61'' telescope can be an essential asset for TDE photometric followup with the inclusion of better time sampled data.
 \end{abstract}
@@
 \section{Introduction}
+One of the most energetic events in the universe occurs when an unfortunate star approaches within the tidal radius of a supermassive black hole (SMBH).
+This is called a tidal disruption event (TDE) and was first theorized by \citet{hills1975}.
+\citet{rees1988} later predicted that the star would be tidally disrupted with $\sim$half of the material circularizing into an accretion disk around the SMBH and the other $\sim$half being ejected from the system as unbound debris.
+The material in the accretion disk should then produce bright, transient X-ray emission as it is accreted onto the SMBH, similar to the picture of an Active Galactic Nuclei.
 
-\section{Methods}
+About a decade later, the first TDE candidates were discovered observationally as bright X-ray transients \citep{donley2002}.
+But, with the advent of large optical all sky surveys, TDEs were also discovered to emit at optical wavelengths \citep{iPTF,ZTF,panstarrstde}.
+The origin of this optical emission from TDEs remains an open question.
+The leading model is inverse compton scattering, typically called ``reprocessing'', of the high energy X-rays by gas in a torus surrounding the SMBH.
+Another possible model is that we are observing optical emission from the ejected material after it escapes the system and cools.
+\citet{gezari2021} provides a more detailed summary of these and additional models.
+
+This boom in the discovery of optically bright TDEs in the past $\sim$decade has resulted in $\sim200$ known TDEs to date, with a current discovery rate of $\sim10/yr$.
+The properties of the TDE emission provides a unique insight into the sub-parsec circumnuclei environment of galaxies and insights into the details of SMBH accretion \citep{holoien2020,Newsome2024}.
+In the optical, many of these properties are extracted using a combination of lightcurve and spectral energy distribution fitting \citep{Mockler2019}.
+Even more, recent population analyses of the lightcurves and spectral evolution of these TDEs show potential correlations between the optical TDE emission and physical properties of the system (e.g.
+\citet{vanVelzen2021}).
+However, more data is needed to verify these potential correlations and distinguish between the potential optical emission models.
+
+Since these correlations are based on $\lesssim 100$ TDEs, they require further exploration with larger datasets to verify.
+As a result, following up TDEs both photometrically and spectroscopically is essential to further our understanding of the relation between TDE emission and the host galaxy and SMBH properties.
+The commonly used modeling softwares, like \citet{Mockler2019}, rely heavily on a well constrained peak in the lightcurve of the TDE.
+This means that observing TDEs with numerous telescopes near peak brightness is essential for future analyses.
+Current all sky surveys, like the Zwicky Transient Facility \citep[ZTF]{ZTF}, provide well time sampled photometry with a few day cadence.
+But, other telescopes can help by observing the TDEs near peak and obtaining even better temporal sampling.
+
+In this work, we observe the TDE AT2024wsd using the Kuiper 61'' telescope on Mt.
+Graham at, or near, peak brightness on the night of 2024-10-18 (local Arizona time); This is the first time the Kuiper 61'' has been used for such observations.
+AT2024wsd, (RA, Dec) = (05:26:38.320, -17:54:54.68), was originally discovered by ZTF on 2024-09-25 11:27:40 (UTC) with a magnitude of 20.0047 \citep{at2024wsd_discovery}.
+ZTF later classified AT2024wsd as a TDE based on the strong Hydrogen emission lines and blue nature of the spectrum \citep{at2024wsd_classification}.
+Our observations of AT2024wsd will contribute to improving the modeling of the TDE emission and will help extract improved constraints on properties of the system like the rise and decay times of the TDE emission, the SMBH mass, the tidally disrupted star mass, and accretion efficiency.
+In turn, these improved constraints will help us better understand the true origin of the optical emission from TDEs.
+
+In \S\ref{sec:method}, we review our observing strategy and data reduction and calibration method.
+In \S\ref{sec:res}, we present the results and lessons learned from this unique opportunity.
+In \S\ref{sec:conclusion}, we summarize our method and results.
+
+\section{Methods}\label{sec:method}
 \subsection{Kuiper 61'' Observations}
+
+\begin{table}
+\caption{Observations Summary}
+\label{tab:obs}
+\begin{tabular}{lllrr}
+\hline
+Image Type & Filter & Start Time (UTC) & Exposure Time (s) & Number of Exposures \\
+\hline
+Target & Harris-B & 08:53:55.552 & 50.00 & 3 \\
+Target & Harris-V & 09:08:13.975 & 50.00 & 3 \\
+Target & Harris-R & 09:03:23.041 & 50.00 & 3 \\
+Target & Bessell-U & 08:58:18.912 & 50.00 & 3 \\
+Flat & Harris-B & 07:53:26.592 & 5.00 & 15 \\
+Flat & Harris-R & 07:46:32.588 & 5.00 & 30 \\
+Flat & Harris-V & 07:57:11.190 & 5.00 & 15 \\
+Flat & Bessell-U & 08:09:02.293 & 30.00 & 15 \\
+Bias & --- & 07:13:58.343 & 0.00 & 31 \\
+Dark & --- & 07:08:36.314 & 30.00 & 5 \\
+Dark & --- & 09:26:19.184 & 5.00 & 5 \\
+Dark & --- & 09:19:58.097 & 50.00 & 5 \\
+\hline
+\end{tabular}
+\end{table}
+
+We observed the TDE AT2024wsd with the Kuiper 61'' telescope on Mt.
+Graham on the night of October 18-19, 2024 (Local Date).
+A summary of the Target and Calibration observations is given in Table \ref{tab:obs}.
+We observed the target with the Mont4k CCD in the Harris- R, B, V and Bessell- U filters.
+These filters are near identical to the standard Johnson/Cousin filter set.
+The flat images were taken with the dome flat capability of the Kuiper 61'' telescope.
+The bias and dark images were taken using standard methods.
+While this telescope is not typically used for transient followup observations, our observing time for class provided a unique opportunity to test it's capabilities.
+
 \subsection{Data Calibration}
+We performed standard bias calibration by stacking the bias images using an average with sigma clipping.
+The sigma clipping uses a $\pm 5 \sigma$ threshold to smooth the images over extreme outliers (e.g.
+hot pixels, cosmic rays, etc.).
+In future calibration steps, we use the same stacking parameters as used for the bias images.
+From the bias images, we estimate the read noise by subtracting off a random bias image from the master bias image ten times to create ten bias difference images.
+Since the bias images include both read noise and persistent detector signal, this renormalizes the bias images and removes extraneous outliers, leaving behind just the extra current due to read noise.
+Finally, we take the standard deviation of all of these images to find the read noise and convert from ADU to electrons using the gain  $G=3.1~e/ADU$ of Mont4k\footnote{https://james.as.arizona.edu/~psmith/61inch/CCD/basicinfo.html}.
+
+After stacking the bias images, we apply the master bias image to each dark image to remove the CCD bias and leave behind just the dark current.
+We then stack the dark images by exposure time, leaving us with a master 5s, 30s, and 50s dark image.
+This is necessary for calibrating the Flat images, which were taken at 5s and 30s, and target images, which were taken at 50s.
+From the dark images, we estimate the dark noise by computing the mean pixel count for each dark image and then performing a linear fit to the mean pixel count as a function of exposure time.
+This gives us a dark current in electrons per pixel per second.
+Since dark current is a poissonian process, we simply take the square root of the dark current to find the dark noise (i.e.
+the shot noise of the dark current) and convert from ADU to electrons using the gain $G=3.1~e/ADU$ of Mont4k.
+
+To calibrate the flat images, we apply the master bias and then the master dark corrections.
+For the Harris- B, R, V flat images we use the 5s dark correction and for the Bessell-U flat image we use the 30s dark correction.
+We then stack the flat images to create one flat for each filter.
+The flats are not used to estimate any of the noise sources.
+
+\begin{figure}[!h]
+  \includegraphics[width=\textwidth]{../analysis/fcal-images.png}
+  \caption{Post-reduction stacked images in the four filters we observed in.
+In the background image, the red square surrounds the zoom in region which includes the aperture, the red circle, overlayed on top of our target.
+The blue circles are the apertures on the foreground sources used for the flux calibration.}
+  \label{fig:targ}
+\end{figure}
+
+Finally, we apply all of these calibrations to the target images.
+First, we bias correct the target images using the master bias.
+Then, we subtract the 50s master dark image from the target images.
+We apply the flat correction to each bias and dark corrected target image for the corresponding filter.
+Then, we stack all of the corrected target images by filter to give 4 science images.
+We then use \texttt{astrometry.net} to compute the WCS solutions for each image.
+From these reduced images, we remove the chip gap by using a scanning method with a tophat kernel that averages over the 4 pixels on either side of the gap.
+This leaves us with the images in Figure \ref{fig:targ}.
 
 \subsection{Signal Extraction and Flux Calibration}
+We compute the sum of the ADU counts from the target using an circular aperture centered at the target coordinates, (RA, Dec) = (05:26:38.320, -17:54:54.68), with a 5'' radius.
+This includes all of the pixels nearby the target with counts that visibly rise above the background and noise.
+The apertures for each filter are shown as red circles in Figure \ref{fig:targ}.
+The counts from each aperture are shown in Figure \ref{fig:aperture-counts}.
+These count histograms appear very Gaussian which likely means we are pushing up against the point spread function (PSF) of the telescope and instrument.
+This means that, as expected, our target can be treated as a point source since it fills the PSF of the telescope.
+To find the sum of the ADU counts within the aperture, we simply integrate over these count histograms.
 
@@
   \includegraphics[width=\textwidth]{../analysis/aperture-counts-hist.png}
-  \caption{Caption}
+  \caption{Distributions of ADU counts in the target apertures for each filter. Each histogram is approximately Gaussian indicating that the target fills the point spread function of the telescope.}
   \label{fig:aperture-counts}
@@
 
-\begin{figure}
-  \includegraphics[width=\textwidth]{../analysis/target-images.png}
-  \caption{Caption}
-  \label{fig:targ}
-\end{figure}
+We convert the sum of the counts from the target plus background to electrons using the gain $G=3.1~e/ADU$.
+Then, to convert from electrons to photons, we assume a throughput $T=85.78\%$ which is derived assuming the primary mirror has a $93\%$ reflectivity and that there are four other optics between the primary mirror and detector that each have an individual throughput of $98\%$.
+Combining these gives a throughput $T=(0.93)(0.98)^4=0.8578$.
+We also assume a constant quantum efficiency $Q=70\%$\footnote{\url{https://lavinia.as.arizona.edu/~tscopewiki/doku.php?id=public:catalinas:bigelow:kuiper_61:mont4k}} that is derived from the approximate average quantum efficiency from 300-700nm.
+Using the throughput and quantum efficiency, we convert from electrons to photons incident on the telescope by multiplying the electron counts by $1/(T \times Q)$.
+These counts, in ADU, electrons, and photons are given in Table \ref{tab:res}.
 
-% \begin{figure}
-%   \includegraphics[width=\textwidth]{../analysis/fcal-images.png}
-%   \caption{Caption}
-%   \label{fig:fcal}
-% \end{figure}
+To estimate the background signal, we use an annulus aperture centered on the target coordinates with an inner radius of 5'' and outer radius of 10''.
+We chose to use an annulus to estimate the background because, by visual inspection of the images, the background rate varies by $\sim300$ counts ($\sim25\%$) across the image.
+This is likely because the target was near the setting moon which created a gradient of background illumination.
+Therefore, we want a local estimate of the background rather than a global one.
+After integrating over the counts in the annulus, we take the average to find the background counts per pixel.
+We then subtract the background counts, multiplied by the area of the target aperture, from the target aperture counts to find the signal coming just from the target itself.
+We follow the same procedure as with the target aperture to convert from ADU to electrons and photons.
+The background estimation and subtraction results are in Table \ref{tab:res}.
 
-\subsection{SED Modeling}
+Once we have a background subtracted signal, we need to convert from photon counts to physical units.
+To do this, we query the VizieR data service for Johnson/Cousins magnitudes in our field of view.
+We follow the same procedure as used for the target for each of these stars in the field of view: 1) place ana 5'' aperture  over each source and find the sum of the counts; 2) Find and subtract the background using an annulus with a 5'' inner radius and 10'' outer radius; and 3) Convert from ADU to electrons and photons.
+The aperture placed on each of these foreground stars is shown as a blue circle in Figure \ref{fig:targ}.
+Each of these foreground stars has synthetic Johnson/Cousins magnitudes generated from the Gaia BP and RP mean spectra of the sources \citep{gaiadr3,gaiadr3_syntphot} (VizieR catalog I/360/syntphot).
+Note that we choose to use the Johnson/Cousins filter system since it is very similar to the Harris and Bessell filters but a more common standard.
+This, of course, introduces a level of systematic uncertainty into our magnitude calculation but this is negligible compared to the  uncertainties on our flux calculations.
+From these synthetic magnitudes, we find the zero point, $f_0$ of each filter using equation \ref{eq:f0},
 
-\section{Results}
+\begin{align}
+  f_{0,\gamma} = f_\gamma \times 10^{0.4 * m_\lambda},\label{eq:f0}
+\end{align}
+
+\noindent where $f_\gamma$ is the photon count flux and $m_\lambda$ is the synthetic magnitude of the source in a given filter.
+
+We take the median of the computed zero points from each of these foreground stars to find a single zero point for the Mont4k detector.
+We choose to use the median to make our zero point calculation robust to outliers like variable stars or possible contaminating galaxies.
+The calculated zero points in photon counts are listed in Table \ref{tab:res}.
+Using the computed zero points we calculate the magnitude for each filter of our source using the standard flux-magnitude equation,
+
+\begin{align}
+  m_\lambda = -2.5\log_{10}\left(\frac{f_\gamma}{f_{\gamma,0}}\right).
+\end{align}
+
+\noindent We compute the uncertainty in these magnitudes using standard error propagation on the noise in the photon count flux,
+
+\begin{align}
+  \sigma_m \approx \frac{\ln(10)}{2.5} \frac{\sigma_{f_\gamma}}{f_\gamma} .
+\end{align}
+
+\noindent The computed apparent magnitudes with uncertainty are given in Table \ref{tab:res} and shown in Figure \ref{fig:lc} with respect to other public photometry of this tidal disruption event.
+
+\subsection{Lightcurve Modeling}
+To compare the magnitudes measured at Kuiper to other public photometry we pull all of the available photometry on the Transient Name Server page for AT2024wsd\footnote{https://www.wis-tns.org/object/2024wsd} which consists mostly of Zwicky Transient Facility (ZTF) preliminary detections.
+The Kuiper photometry and public photometry are shown for comparison in Figure \ref{fig:lc}.
+We also query the Asteroid Terrestrial-impact Last Alert System (ATLAS) forced photometry service for archival photometry of this target.
+The ATLAS query revealed all nondetections, which are also shown in Figure \ref{fig:lc}.
+To compare the public photometry to our Kuiper data, we assume that the measurements in the Johnson/Cousins filters are similar to those made in the ZTF b, g, and r filters because the effective wavelengths tend to be within a few hundred angstroms.
+There are obviously limitations to this assumption but it is our only option given the lack of {\it public} photometry for this object.
+There is no public photometry available for the Bessell-U filter so we are unable to derive rise rates for this filter.
+
+Since there are only one or two additional public photometry points for AT2024wsd, we are only able to apply a simple linear fit to the brightening of the transient.
+We do this by using a $\chi^2$ fit of a linear model $m = m_0 + kt$, where $k$ is the brightening rate in magnitudes per day, to the data.
+This fit gives us a brightening rate of the transient and, assuming that we observed at or near peak brightness, a rise time for the brightening of the transient.
+
+\section{Results \& Discussion}\label{sec:res}
 \subsection{Observational Results}
@@
 \begin{table}
+  \centering
   \caption{Reduction Results}
@@
   \begin{tabular}{lllll}
-Filter & Harris-V & Bessell-U & Harris-B & Harris-R \\
-Source Aperture Sum (ADU) & 525131.38 & 95118.46 & 352222.45 & 554880.18 \\
-Source Aperture Sum (e) & 1627907.28 & 294867.23 & 1091889.60 & 1720128.57 \\
-Source Aperture Sum ($\gamma$) & 2711100.28 & 491068.91 & 1818421.88 & 2864684.69 \\
-Background Annulus Sum (ADU) & 521430.41 & 94325.44 & 348674.99 & 549048.02 \\
-Background Annulus Sum (e) & 1616434.28 & 292408.86 & 1080892.45 & 1702048.85 \\
-Background Annulus Sum ($\gamma$) & 2691993.26 & 486974.75 & 1800107.34 & 2834574.90 \\
-Dark Noise ($\sigma_D$; ADU) & 0.29 & 0.29 & 0.29 & 0.29 \\
-Dark Noise ($\sigma_D$; e) & 0.51 & 0.51 & 0.51 & 0.51 \\
-Read Noise ($\sigma_R$; ADU) & 3.26 & 3.26 & 3.26 & 3.26 \\
-Read Noise ($\sigma_R$; e) & 10.10 & 10.10 & 10.10 & 10.10 \\
-Signal ($f_e$; e) & 11473.00 & 2458.37 & 10997.15 & 18079.72 \\
-Signal ($f_\gamma$; $\gamma$) & 19107.02 & 4094.15 & 18314.54 & 30109.79 \\
-SNR & 8.74 & 3.94 & 10.10 & 13.42 \\
-Zero Point ($10^{12}f_0$; $\gamma$) & 0.47 & 0.05 & 0.33 & 0.44 \\
-Apparent Magnitude & 18.48 & 17.72 & 18.14 & 17.92 \\
-Apparent Magnitude Error & 2.11 & 4.49 & 1.80 & 1.34 \\
+    \hline
+    Filter & Harris-B & Harris-V & Harris-R & Bessell-U \\
+    \hline
+    Source Aperture Sum (ADU) & 351531.39 & 524268.83 & 554351.81 & 94429.37 \\
+    Source Aperture Sum (e) & 1089747.30 & 1625233.38 & 1718490.61 & 292731.06 \\
+    Source Aperture Sum ($\gamma$) & 1814854.11 & 2706647.21 & 2861956.85 & 487511.34 \\
+    \hline
+    Background Annulus Sum (ADU) & 348945.20 & 522267.83 & 549786.75 & 93693.18 \\
+    Background Annulus Sum (e) & 1081730.11 & 1619030.28 & 1704338.91 & 290448.86 \\
+    Background Annulus Sum ($\gamma$) & 1801502.37 & 2696316.62 & 2838388.76 & 483710.59 \\
+    \hline
+    Dark Noise ($\sigma_D$; ADU/pixel) & 0.29 & 0.29 & 0.29 & 0.29 \\
+    Dark Noise ($\sigma_D$; e/pixel) & 0.51 & 0.51 & 0.51 & 0.51 \\
+    \hline
+    Read Noise ($\sigma_R$; ADU/pixel) & 3.04 & 3.04 & 3.04 & 3.04 \\
+    Read Noise ($\sigma_R$; e/pixel) & 9.41 & 9.41 & 9.41 & 9.41 \\
+    \hline
+    Signal ($f_e$; e) & 8017.18 & 6203.11 & 14151.70 & 2282.20 \\
+    Signal ($f_\gamma$; $\gamma$) & 13351.74 & 10330.59 & 23568.10 & 3800.75 \\
+    Zero Point ($10^{12}f_0$; $\gamma$) & 0.31 & 0.46 & 0.44 & 0.05 \\
+    Apparent Magnitude & 18.41 & 19.12 & 18.18 & 17.74 \\
+    Apparent Magnitude Error & 0.12 & 0.19 & 0.09 & 0.23 \\
+    \hline
+    SNR & 7.55 & 4.81 & 10.68 & 3.96 \\
+    \hline
   \end{tabular}
@@
 
-This is where things like SNR and extracted magnitudes will go
+A summary of our data reduction and zero point calibration results is in table \ref{tab:res}.
+From these calibrations, we compute a signal-to-noise ratio, derived both theoretically (\S\ref{sec:snr_theory}) and observationally (\S\ref{sec:snr_obs}), in the subsequent sections.
 
-\subsection{Modeling Results}
+\subsubsection{Theoretical SNR Calculations}\label{sec:snr_theory}
+Prior to observing, we computed the theoretical observing time using the standard SNR equation, equation \ref{eq:snr},
 
-\section{Conclusions}
+\begin{align}
+  SNR = \frac{N_e}{\sqrt{N_e + n_{pix}f_{bkgd}t_{exp} + n_{pix}t_{exp}D + n_{pix}R^2 }}, \label{eq:snr}
+\end{align}
+where $f_e$ is the electron count flux, $n_{pix}$ is the number of pixels in the aperture, $f_{bkgd}$ is the background electron count flux, $t_{exp}$ is the exposure time, $D$ is the dark current, and $R$ is the read noise.
+To find the exposure time, we use the sky brightness estimate, $m_{bkgd}=22 mag/as^2$; standard read noise, $R=5~e$; dark current, $D=16.6 e/pix/hr$; gain $G=3.1 e/ADU$; quantum efficiency, $Q=0.88$; and throughput, $T=0.8578$.
+Using these values, we solve equation \ref{eq:snr} as a quadratic and find that for an SNR of 10 for a target with visible magnitude $V\sim18$, the exposure time on the Kuiper telescope with the Mont4k detector is $t_{exp} \sim 0.01s$.
+
+\subsubsection{Observed SNR Calculation}\label{sec:snr_obs}
+To observationally estimate the SNR of our measurement of AT2024wsd, we use a modified version of equation \ref{eq:snr},
+
+\begin{align}
+  SNR = \frac{N_e}{\sqrt{N_e+N_{bkgd}+n_{pix}\left(D + R^2\right)}},
+\end{align}
+
+\noindent where we combine the background noise term into simply the counts in the background annulus, $N_{bkgd}$.
+Filling in values from Table \ref{tab:res}, we find the SNRs per filter given in the last row of Table \ref{tab:res}.
+These SNRs are comparable to the SNR$\sim10$ used in the theoretical calculations.
+However, we used three 50s exposures in each filter instead of the theoretical exposure time $t\sim0.01s$.
+This is likely because our noise is significantly dominated by our background and shot noise rather than the read and dark noise.
+In particular, the poissonian background noise is significantly higher than we theoretically estimated, likely because the target was very close to the moon.
+Additionally, but likely less of a cause of this discrepancy, is that both the dark and read noise seem to be $\sim2$ times larger than the values presented in the Mont4k documentation.
+This is most likely because those values were found in an isolated environment rather than true observing environment.
+
+\subsection{Zero Point Calibration and Lightcurve Fit Results}
+\begin{figure}
+  \includegraphics[width=\textwidth]{../analysis/lightcurve.png}
+  \label{fig:lc}
+  \caption{Light curve, or magnitude as a function of days since discovery, of both the publicly available photometry (circles) and photometry (squares) from this work.
+ATLAS upperlimits are shown as downward facing triangles in both their cyan filter and orange filter.
+The best fit linear rise models are shown as dashed lines where the color corresponds to the color of the data points it is a fit for.}
+\end{figure}
+
+The magnitudes and photon count flux zero points that we computed are given in Table \ref{tab:res}.
+These results are also shown in comparison to publicly available photometry in Figure \ref{fig:lc}.
+As expected, the magnitudes we computed are brighter than the publicly released magnitudes because the transient brightness was likely near peak brightness during our observation.
+
+The best linear model to the data is displayed in Figure \ref{fig:lc} as dashed lines.
+The results of the fits, with uncertainties, are given as text in the top of the figure.
+All fits are relatively poorly constrained given the lack of data.
+But, in particular, the red filter data are very poorly constrained with only two photometry points.
+Therefore, we place limited faith in the rise rates presented in Figure \ref{fig:lc}.
+Even still, using these fits, we can estimate the rise time of this TDE as $t_{rise} \sim 20$ days, an especially interesting quantity since past works have shown that it can be related to the supermassive black hole mass \citep{vanVelzen2021}.
+However, this rise time should be considered a lower limit on the true rise time since our data does not include any photometry on the decay of the light curve.
+
+\subsection{Limitations and Lessons Learned}
+
+The primary lesson learned from this work is that the exposure time computed with the theoretical SNR equation \ref{eq:snr} is likely unreliable for the Kuiper 61'' telescope based on the standard noise sources.
+In the future, it would be beneficial to include a better estimate of the background brightness and slightly higher values for the read and dark noise.
+
+Another important limitation of this work is the comparison of the Harris and Bessell filter system to the Johnson/Cousins and ZTF filter systems.
+Ideally, we would need to perform a bolometric correction to apply to the Harris and Bessell filters on Mont4k to convert them properly to the Johnson/Cousins and ZTF filters.
+This is especially necessary because the Harris and Bessell filters are non-standard, unlike the Johnson/Cousins filter system.
+Future work would include a more robust analysis of this conversion, including the bolometric conversion, rather than assuming the Harris and Bessell filters are similar to the Johnson/Cousins system.
+
+Another important lesson from this is that the Kuiper telescope is not optimized for photometric follow up of transient events.
+This is because we would need nearly nightly, or at least weekly, time on the telescope to improve our temporal sampling of the lightcurve.
+Or, using some Kuiper observations in combination with the more complete, but private, ATLAS and ZTF datasets.
+In the end, because ZTF and ATLAS follow up these transients on a nightly basis, it would probbaly make more sense to let them get the photometry and we use Kuiper for spectrographic followup and classification of transients in the future.
+
+Finally, It is important to note that in the literature the rise rate and rise time of tidal disruption events is typically found with a gaussian fit to the data \citep{gezari2021, vanVelzen2021}.
+However, with our limited dataset, such a fit would be nearly impossible to perform.
+In the future, it would, once again, be beneficial to include a better temporally sampled dataset to better constrain the peak, and therefore rise time, of the lightcurve.
+
+\section{Conclusions}\label{sec:conclusion}
+
+In this work we used the Kuiper 61'' telescope to perform photometric follow up of a tidal disruption event, AT2024wsd, for the first time.
+We observed the TDE in four filters, Harris- B, V, R and Bessell-U, with 3 exposures, each with an exposure time of 50s.
+We then reduced the images using standard procedures.
+We calibrated the flux of AT2024wsd by deriving a photon count zero point using publicly available Johnson/Cousins magnitudes of foreground stars.
+
+The results of these observations are explained in detail in \S\ref{sec:res}.
+Our signal to noise ratio ranges from $\sim4$ to $\sim10$ depending on the filter used.
+The magnitudes we found are about 1 mag brighter than previous public photometry.
+This was expected since the rise time of TDE optical emission tends to be around a month and we were observing AT2024wsd about 3 weeks after initial discovery.
+Using a combination of our photometry and previous public photometry, we find a gradual rise to the approximate peak brightness around $20$ days after discovery of about $-0.05$ mag/day, depending on the filter used.
+This rise rate was derived using a linear fit to our limited dataset and is poorly constrained.
+This rise time reported here should be treated as a lower limit since we have no photometry during the lightcurve decay.
+
+Overall, this work has shown that the Kuiper 61'' telescope can be a valuable asset for photometric follow up of tidal disruption events.
+After the Kuiper telesope is equipped with a spectrograph, future work should also explore the use of the telescope for specotroscopic follow up.
+Future analyses should also work with the ZTF and ATLAS collaborations to generate a better temporally sampled light curve of the transient event.
+Or, similarly, convert the Kuiper telescope to a robotic observatory to scan the entire sky each night (or every few nights).
+This will allow for more detailed modeling and the extraction of more interesting parameters of the disrupting system, like the SMBH mass and accretion properties.
+
+\bibliographystyle{aasjournal}
+\bibliography{main}
 

### 2024-12-16 ASTR518/project/paper/main.tex
add files for submission

@@
 \usepackage{natbib}
+\usepackage{longtable}
+
+% some journal abbreviations for the bib file
+\newcommand\AJ{AJ}%        % Astronomical Journal
 
@@
 \citet{rees1988} later predicted that the star would be tidally disrupted with $\sim$half of the material circularizing into an accretion disk around the SMBH and the other $\sim$half being ejected from the system as unbound debris.
-The material in the accretion disk should then produce bright, transient X-ray emission as it is accreted onto the SMBH, similar to the picture of an Active Galactic Nuclei.
+The material in the accretion disk should then produce bright, transient X-ray emission as it is accreted onto the SMBH.
 
 About a decade later, the first TDE candidates were discovered observationally as bright X-ray transients \citep{donley2002}.
-But, with the advent of large optical all sky surveys, TDEs were also discovered to emit at optical wavelengths \citep{iPTF,ZTF,panstarrstde}.
-The origin of this optical emission from TDEs remains an open question.
+More recently, with the advent of large optical all sky surveys, TDEs were also discovered to emit at optical wavelengths \citep{iPTF,ZTF,panstarrstde}.
+The origin of this optical emission from TDEs remains an open question (2020 Decadel Survey, Subsection B-Q2a).
 The leading model is inverse compton scattering, typically called ``reprocessing'', of the high energy X-rays by gas in a torus surrounding the SMBH.
@@
 The properties of the TDE emission provides a unique insight into the sub-parsec circumnuclei environment of galaxies and insights into the details of SMBH accretion \citep{holoien2020,Newsome2024}.
-In the optical, many of these properties are extracted using a combination of lightcurve and spectral energy distribution fitting \citep{Mockler2019}.
-Even more, recent population analyses of the lightcurves and spectral evolution of these TDEs show potential correlations between the optical TDE emission and physical properties of the system (e.g.
+In the optical, many of these properties are extracted using a combination of light-curve and spectral energy distribution fitting \citep{Mockler2019}.
+Even more, recent population analyses of the light-curves and spectral evolution of these TDEs show potential correlations between the optical TDE emission and physical properties of the system (e.g.
 \citet{vanVelzen2021}).
@@
 As a result, following up TDEs both photometrically and spectroscopically is essential to further our understanding of the relation between TDE emission and the host galaxy and SMBH properties.
-The commonly used modeling softwares, like \citet{Mockler2019}, rely heavily on a well constrained peak in the lightcurve of the TDE.
+The commonly used modeling softwares, like \citet{Mockler2019}, rely heavily on a well constrained peak in the light-curve of the TDE.
 This means that observing TDEs with numerous telescopes near peak brightness is essential for future analyses.
@@
 \begin{table}
+  \centering
   \caption{Observations Summary}
@@
 We observed the target with the Mont4k CCD in the Harris- R, B, V and Bessell- U filters.
-These filters are near identical to the standard Johnson/Cousin filter set.
 The flat images were taken with the dome flat capability of the Kuiper 61'' telescope.
@@
 Since the bias images include both read noise and persistent detector signal, this renormalizes the bias images and removes extraneous outliers, leaving behind just the extra current due to read noise.
-Finally, we take the standard deviation of all of these images to find the read noise and convert from ADU to electrons using the gain  $G=3.1~e/ADU$ of Mont4k\footnote{https://james.as.arizona.edu/~psmith/61inch/CCD/basicinfo.html}.
+Finally, we take the standard deviation of all of these images to find the read noise and convert from ADU to electrons using the gain  $G=3.1~e/ADU$ of Mont4k\footnote{\url{https://james.as.arizona.edu/~psmith/61inch/CCD/basicinfo.html}}.
 
@@
 Then, we stack all of the corrected target images by filter to give 4 science images.
-We then use \texttt{astrometry.net} to compute the WCS solutions for each image.
+We then use \texttt{astrometry.net} \citep{lang2010} to compute the WCS solutions for each image.
 From these reduced images, we remove the chip gap by using a scanning method with a tophat kernel that averages over the 4 pixels on either side of the gap.
@@
 To do this, we query the VizieR data service for Johnson/Cousins magnitudes in our field of view.
-We follow the same procedure as used for the target for each of these stars in the field of view: 1) place ana 5'' aperture  over each source and find the sum of the counts; 2) Find and subtract the background using an annulus with a 5'' inner radius and 10'' outer radius; and 3) Convert from ADU to electrons and photons.
+We follow the same procedure as used for the target for each of these stars in the field of view: 1) place a 5'' aperture  over each source and find the sum of the counts; 2) Find and subtract the background using an annulus with a 5'' inner radius and 10'' outer radius; and 3) Convert from ADU to electrons and photons.
 The aperture placed on each of these foreground stars is shown as a blue circle in Figure \ref{fig:targ}.
+We did this for 19 foreground stars and the results of the aperture photometry and background annulus estimation for one source are given in Table \ref{tab:res}.
+
 Each of these foreground stars has synthetic Johnson/Cousins magnitudes generated from the Gaia BP and RP mean spectra of the sources \citep{gaiadr3,gaiadr3_syntphot} (VizieR catalog I/360/syntphot).
@@
 
-We take the median of the computed zero points from each of these foreground stars to find a single zero point for the Mont4k detector.
+\noindent We take the median of the computed zero points from each of these foreground stars to find a single zero point for the Mont4k detector.
 We choose to use the median to make our zero point calculation robust to outliers like variable stars or possible contaminating galaxies.
@@
 
-\subsection{Lightcurve Modeling}
+\subsection{Light-Curve Modeling}
 To compare the magnitudes measured at Kuiper to other public photometry we pull all of the available photometry on the Transient Name Server page for AT2024wsd\footnote{https://www.wis-tns.org/object/2024wsd} which consists mostly of Zwicky Transient Facility (ZTF) preliminary detections.
@@
   \label{tab:res}
-  \begin{tabular}{lllll}
+  \begin{longtable}{lllll}
     \hline
-    Filter & Harris-B & Harris-V & Harris-R & Bessell-U \\
+    Filter & Harris-R & Harris-B & Harris-V & Bessell-U \\
     \hline
-    Source Aperture Sum (ADU) & 351531.39 & 524268.83 & 554351.81 & 94429.37 \\
-    Source Aperture Sum (e) & 1089747.30 & 1625233.38 & 1718490.61 & 292731.06 \\
-    Source Aperture Sum ($\gamma$) & 1814854.11 & 2706647.21 & 2861956.85 & 487511.34 \\
+    Source Aperture Sum (ADU) & 554351.81 & 351531.39 & 524268.83 & 94429.37 \\
+    Source Aperture Sum (e) & 1718490.61 & 1089747.30 & 1625233.38 & 292731.06 \\
+    Source Aperture Sum ($\gamma$) & 2861956.85 & 1814854.11 & 2706647.21 & 487511.34 \\
     \hline
-    Background Annulus Sum (ADU) & 348945.20 & 522267.83 & 549786.75 & 93693.18 \\
-    Background Annulus Sum (e) & 1081730.11 & 1619030.28 & 1704338.91 & 290448.86 \\
-    Background Annulus Sum ($\gamma$) & 1801502.37 & 2696316.62 & 2838388.76 & 483710.59 \\
+    Background Annulus Sum (ADU) & 548693.02 & 348232.62 & 521197.05 & 93495.58 \\
+    Background Annulus Sum (e) & 1700948.36 & 1079521.11 & 1615710.86 & 289836.31 \\
+    Background Annulus Sum ($\gamma$) & 2832742.16 & 1797823.52 & 2690788.50 & 482690.45 \\
     \hline
@@
     \hline
-    Read Noise ($\sigma_R$; ADU/pixel) & 3.04 & 3.04 & 3.04 & 3.04 \\
-    Read Noise ($\sigma_R$; e/pixel) & 9.41 & 9.41 & 9.41 & 9.41 \\
+    Read Noise ($\sigma_R$; ADU/pixel) & 3.15 & 3.15 & 3.15 & 3.15 \\
+    Read Noise ($\sigma_R$; e/pixel) & 9.76 & 9.76 & 9.76 & 9.76 \\
     \hline
-    Signal ($f_e$; e) & 8017.18 & 6203.11 & 14151.70 & 2282.20 \\
-    Signal ($f_\gamma$; $\gamma$) & 13351.74 & 10330.59 & 23568.10 & 3800.75 \\
-    Zero Point ($10^{12}f_0$; $\gamma$) & 0.31 & 0.46 & 0.44 & 0.05 \\
-    Apparent Magnitude & 18.41 & 19.12 & 18.18 & 17.74 \\
-    Apparent Magnitude Error & 0.12 & 0.19 & 0.09 & 0.23 \\
+    Target Signal ($f_e$; e) & 17542.25 & 10226.19 & 9522.52 & 2894.75 \\
+    Target Signal ($f_\gamma$; $\gamma$) & 29214.69 & 17030.59 & 15858.71 & 4820.89 \\
+    Noise on Target (e) & 1326.70 & 1063.67 & 1291.08 & 578.25 \\
+    SNR for Target & 13.22 & 9.61 & 7.38 & 5.01 \\
     \hline
-    SNR & 7.55 & 4.81 & 10.68 & 3.96 \\
+    Sample Flux Cal.
+Aperture Sum (ADU)\footnote{This from 1 of the 19 foreground stars used to estimate the zero point.
+The others are available upon request.} & 786324.66 & 413693.58 & 692494.86 & 102921.67 \\
+    Sample Flux Cal. Background Annulus Sum (ADU) & 583842.18 & 356051.85 & 543212.76 & 94262.53 \\
+    Sample Flux Cal. Signal (ADU) & 202482.48 & 57641.73 & 149282.10 & 8659.14 \\
+    Sample Flux Cal. Signal (e) & 627695.68 & 178689.35 & 462774.51 & 26843.33 \\
+    Sample Flux Cal. Signal ($\gamma$) & 1045358.02 & 297587.43 & 770699.97 & 44704.61 \\
+    Sample Flux Cal. Noise (e) & 1574.56 & 1150.69 & 1479.32 & 600.58 \\
     \hline
-  \end{tabular}
+    Zero Point ($10^{12}f_0$; $\gamma$) & 0.44 & 0.32 & 0.47 & 0.05 \\
+    Apparent Magnitude & 17.95 & 18.18 & 18.67 & 17.51 \\
+    Apparent Magnitude Error & 0.07 & 0.10 & 0.12 & 0.18 \\
+    \hline
+  \end{longtable}
+  \centering
+  \vspace{-0.75cm}
 \end{table}
-
 A summary of our data reduction and zero point calibration results is in table \ref{tab:res}.
@@
 
-\subsection{Zero Point Calibration and Lightcurve Fit Results}
+\subsection{Zero Point Calibration and Light-Curve Fit Results}
 \begin{figure}
@@
 Another important lesson from this is that the Kuiper telescope is not optimized for photometric follow up of transient events.
-This is because we would need nearly nightly, or at least weekly, time on the telescope to improve our temporal sampling of the lightcurve.
+This is because we would need nearly nightly, or at least weekly, time on the telescope to improve our temporal sampling of the light-curve.
 Or, using some Kuiper observations in combination with the more complete, but private, ATLAS and ZTF datasets.
-In the end, because ZTF and ATLAS follow up these transients on a nightly basis, it would probbaly make more sense to let them get the photometry and we use Kuiper for spectrographic followup and classification of transients in the future.
+In the end, because ZTF and ATLAS follow up these transients on a nightly basis, it would probably make more sense to let them get the photometry and we use Kuiper for spectrographic followup and classification of transients in the future.
 
@@
 However, with our limited dataset, such a fit would be nearly impossible to perform.
-In the future, it would, once again, be beneficial to include a better temporally sampled dataset to better constrain the peak, and therefore rise time, of the lightcurve.
+In the future, it would, once again, be beneficial to include a better temporally sampled dataset to better constrain the peak, and therefore rise time, of the light-curve.
 
@@
 
-The results of these observations are explained in detail in \S\ref{sec:res}.
+The results of these observations are explained in detail in \S\ref{sec:res} and given in Table \ref{tab:res}.
 Our signal to noise ratio ranges from $\sim4$ to $\sim10$ depending on the filter used.
@@
 This rise rate was derived using a linear fit to our limited dataset and is poorly constrained.
-This rise time reported here should be treated as a lower limit since we have no photometry during the lightcurve decay.
+This rise time reported here should be treated as a lower limit since we have no photometry during the light-curve decay.
 
@@
 This will allow for more detailed modeling and the extraction of more interesting parameters of the disrupting system, like the SMBH mass and accretion properties.
+
+\software{
+  \citet{lang2010},
+  \citet{photutils},
+  \citet{ccdproc},
+  \citet{astropy:2022},
+  \citet{numpy},
+  \citet{pandas-ds},
+  \citet{pandas-zenodo}
+}
 

### 2025-03-05 ASTR518/hw/HW1/Franz_ASTR518_HW1_Q1.tex
updates

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage{mathalpha}
\usepackage[caption=false]{subfig}
\usepackage{fancyhdr}
\usepackage[margin=1in, headsep=36pt]{geometry}
\usepackage{hyperref}
\usepackage{cancel}
\usepackage{natbib}
\usepackage{longtable}

\bibliographystyle{unsrtnat}

\def\title{Homework 1}
\def\author{Noah Franz}
\def\duedate{Sept. 18, 2024}
\def\class{ASTR518}

\fancypagestyle{hdr}
{
    \fancyhead[L]{\fontsize{16}{18}\selectfont \author \\ Due Date: \duedate }
    \fancyhead[R]{\fontsize{16}{18}\selectfont  \title \\ \class}
}

\begin{document}

\thispagestyle{hdr}

{\it \large Practice Science Motivation (1 page)}

\begin{table}[!ht]
    \centering
    \caption{Summary of Subfields Supported by TDE Science}
    \label{tab:motivation}
    \begin{tabular}{p{4cm} p{3cm} p{8cm}}
    \hline
        Astronomical Subfield & Decadal Subsection & How TDE Observations are Useful \\
        \hline
        TDE Emission & B-Q2a & --- \\
        Transients Powered by Black Holes & B-Q2a & Since TDEs are powered by Black Holes, they are directly applicable. \\
        Multimessenger astronomy & B-DA8 & There has been some evidence of neutrino detections from nearby TDEs. \\
        \hline \\ 
        Galaxy Nuclei & D-Q4d & Radio observations of TDEs provide circumnuclear ($r < 1~\textrm{pc}$) contents and density profiles. \\
        Black Holes & B-Q2a, B-Q4b, D-Q3b,  & TDEs provide measurement of the mass of a central SMBH independent of galaxy properties and scaling relations (e.g. M-$\sigma$). They also provide a means to discover and study the elusive intermediate mass black hole. \\
        Shock Physics & B-Q2b & Radio observations of TDEs reveal the properties of the shock front as it propagates through the circumnuclear medium. \\
        Jet Physics & B-Q2a, B-Q3a & Prompt radio observations of TDEs will capture the early-time jet evolution minutes to days after the initial launch. \\
         \hline 
    \end{tabular}
\end{table}

\indent A primary science goal of the 2023 Astronomy Decadal, and a personal interest of mine, is the continued prompt multiwavelength followup of transient events. These violent and explosive transient events provide a unique probe of high energy phenomenon and environments that are impossible to reproduce on the surface of the Earth. Of particular interest are tidal disruption events (TDEs). TDEs occur when a star approaches within the tidal radius of a supermassive black hole (SMBH) and is torn apart, releasing emission across the electromagnetic spectrum. Understanding the emission from TDEs on their own and how it relates to other transient emission is an open question in astronomy and a key focus of the 2023 Astronomy Decadal. The relevant Decadal subsections are listed in the first part of Table \ref{tab:motivation}.

\indent Studying TDEs will not only further our understanding of them but also many other areas of astronomy. For instance, studying TDE emission provides a probe the SMBH properties, the sub-parsec galactic nuclei environment, jet evolution and fundamental physics, and shock physics. For instance, using radio observations of TDEs we are able to study the density and particle makeup of the previously quiescent galactic nuclei. A summary of areas of astronomy probed by TDE observations, as well as the relevant Atronomy 2020 Decadel (sub)sections corresponding to each of these areas, is given in Table \ref{tab:motivation}. Overall, this makes multiwavelength observations of TDEs necessary to further our fundamental understanding of high energy, dense astronomical environments.

\indent In particular, as described in Table \ref{tab:motivation}, prompt radio/millimeter observations of TDEs allow us to study the early evolution of jets. As the jets evolve outwards, they shock the previously quiescent circumnuclear medium, producing synchrotron emission visible in the radio and millimeter. Fitting a \textit{complete} spectral energy distribution of TDEs allows us to extract properties of the jet, shock front, and ambient circumnuclear medium. Since this SED normally peaks around 1-10 GHz (depending on the time of the observation), observations with sensitive telescopes like the Very Large Array (VLA) and Atacama Large Millimeter Array (ALMA) necessary to study TDE radio/millimeter emission and further our understanding of jet evolution. A list of recently radio bright TDEs is given in Table \ref{tab:tdes} as examples of objects that require followup. Although, for a true study of this nature, we would need ``Target of Opportunity" (ToO) observations within days after the initial optical or X-ray detection.    
\begin{longtable}{l c c c p{4.5cm}}

    % \centering \\
    \caption{Sample of Radio Bright TDEs for Observations} \\
    \label{tab:tdes} \\

     \hline \\
     IAU Name & RA [hours] & Declination [degree] & Redshift & Approximate Flux Density at 6GHz [$\mu$Jy] \\
     \hline \\
     AT2022dyt & 10:00:08.008 & +26:27:38.57 & 0.072 & 75 \\
     AT2022wtn & 23:23:23.778 & +10:41:07.99	& 0.049 & 300 \\
     AT2021sdu & 01:11:23.924 & +50:34:29.67 & 0.059 & 75 \\
     AT2020zso & 22:22:17.130 & -07:15:59.08 & 0.061 & 150 \\
     AT2018cqh & 02:33:46.930 & -01:01:28.38 & ---\footnote{No redshift publicly available for AT2018cqh on the Transient Name Server (TNS).} & $10^5$\\
     AT2018hyz & 10:06:50.871 & +01:41:34.08 & 0.04573 & $10^5$\\
     \hline \\
\end{longtable}

\end{document}

### 2025-03-05 ASTR518/hw/HW1/Franz_ASTR518_HW1_Q1_Edits.tex
updates

--- 2025-03-05 ASTR518/hw/HW1/Franz_ASTR518_HW1_Q1.tex
@@
 
-\begin{table}[!ht]
-    \centering
-    \caption{Summary of Subfields Supported by TDE Science}
-    \label{tab:motivation}
-    \begin{tabular}{p{4cm} p{3cm} p{8cm}}
-    \hline
-        Astronomical Subfield & Decadal Subsection & How TDE Observations are Useful \\
-        \hline
-        TDE Emission & B-Q2a & --- \\
-        Transients Powered by Black Holes & B-Q2a & Since TDEs are powered by Black Holes, they are directly applicable. \\
-        Multimessenger astronomy & B-DA8 & There has been some evidence of neutrino detections from nearby TDEs. \\
-        \hline \\ 
-        Galaxy Nuclei & D-Q4d & Radio observations of TDEs provide circumnuclear ($r < 1~\textrm{pc}$) contents and density profiles. \\
-        Black Holes & B-Q2a, B-Q4b, D-Q3b,  & TDEs provide measurement of the mass of a central SMBH independent of galaxy properties and scaling relations (e.g.
+% \begin{table}[!ht]
+%     \centering
+%     \caption{Summary of Subfields Supported by TDE Science}
+%     \label{tab:motivation}
+%     \begin{tabular}{p{4cm} p{3cm} p{8cm}}
+%     \hline
+%         Astronomical Subfield & Decadal Subsection & How TDE Observations are Useful \\
+%         \hline
+%         TDE Emission & B-Q2a & --- \\
+%         Transients Powered by Black Holes & B-Q2a & Since TDEs are powered by Black Holes, they are directly applicable. \\
+%         Multimessenger astronomy & B-DA8 & There has been some evidence of neutrino detections from nearby TDEs. \\
+%         \hline \\ 
+%         Galaxy Nuclei & D-Q4d & Radio observations of TDEs provide circumnuclear ($r < 1~\textrm{pc}$) contents and density profiles. \\
+%         Black Holes & B-Q2a, B-Q4b, D-Q3b,  & TDEs provide measurement of the mass of a central SMBH independent of galaxy properties and scaling relations (e.g.
 M-$\sigma$).
@@
 \\
-        Shock Physics & B-Q2b & Radio observations of TDEs reveal the properties of the shock front as it propagates through the circumnuclear medium. \\
-        Jet Physics & B-Q2a, B-Q3a & Prompt radio observations of TDEs will capture the early-time jet evolution minutes to days after the initial launch. \\
-         \hline 
-    \end{tabular}
-\end{table}
+%         Shock Physics & B-Q2b & Radio observations of TDEs reveal the properties of the shock front as it propagates through the circumnuclear medium. \\
+%         Jet Physics & B-Q2a, B-Q3a & Prompt radio observations of TDEs will capture the early-time jet evolution minutes to days after the initial launch. \\
+%          \hline 
+%     \end{tabular}
+% \end{table}
 
-\indent A primary science goal of the 2023 Astronomy Decadal, and a personal interest of mine, is the continued prompt multiwavelength followup of transient events.
+\indent A primary science goal of the 2023 Astronomy Decadal is the continued prompt multiwavelength followup of transient events.
 These violent and explosive transient events provide a unique probe of high energy phenomenon and environments that are impossible to reproduce on the surface of the Earth.
-Of particular interest are tidal disruption events (TDEs).
+Of particular interest are tidal disruption events (TDEs; 2023 Decadel, Subsection B-Q2a).
 TDEs occur when a star approaches within the tidal radius of a supermassive black hole (SMBH) and is torn apart, releasing emission across the electromagnetic spectrum.
 Understanding the emission from TDEs on their own and how it relates to other transient emission is an open question in astronomy and a key focus of the 2023 Astronomy Decadal.
-The relevant Decadal subsections are listed in the first part of Table \ref{tab:motivation}.
 
@@
 For instance, studying TDE emission provides a probe the SMBH properties, the sub-parsec galactic nuclei environment, jet evolution and fundamental physics, and shock physics.
-For instance, using radio observations of TDEs we are able to study the density and particle makeup of the previously quiescent galactic nuclei.
-A summary of areas of astronomy probed by TDE observations, as well as the relevant Atronomy 2020 Decadel (sub)sections corresponding to each of these areas, is given in Table \ref{tab:motivation}.
+For instance, using radio observations of TDEs we are able to study the density and particle makeup of the previously quiescent galactic nuclei at a sub-parsec scale(2023 Decadel, Section D-Q4d).
+Studying the density and structure of the galactic nuclei on such small scales will help us better understand both SMBH accretion and how it affects the evolution and structure of galaxies as a while.
 Overall, this makes multiwavelength observations of TDEs necessary to further our fundamental understanding of high energy, dense astronomical environments.
 
-\indent In particular, as described in Table \ref{tab:motivation}, prompt radio/millimeter observations of TDEs allow us to study the early evolution of jets.
+\indent In particular, prompt radio/millimeter observations of TDEs allow us to study the early evolution of jets (2023 Decadel, Subsections B-Q2a and B-Q3a).
 As the jets evolve outwards, they shock the previously quiescent circumnuclear medium, producing synchrotron emission visible in the radio and millimeter.
@@
 \begin{longtable}{l c c c p{4.5cm}}    
-
-    % \centering \\
+    \centering \\
     \caption{Sample of Radio Bright TDEs for Observations} \\
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: LaTeX
+%%% TeX-master: t
+%%% End:
